---
title: "Synthetic Mentoring Pairing by Gale-Shapley Algorithm - `r params$year`"
author: "Synthetic Analysis"
date: "`r Sys.Date()`"
params:
  year: 2023
  u: 0.90         # weight on overall_survey_match_num
  heavy: false    # run time-expensive chunks?
  artifacts_dir: "artifacts"  # <— NEW: base output folder (runner will create subfolders per u)
  seed: 88        # RNG seed: mentor-duplication sampling and score-tie jitter
output:
  html_document:
    code_folding: "hide"
    toc: yes
---

<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

# Data Setup for this HTML 

This Rmd can also be rendered independently for a single synthetic input year instead of running the full batch script.

Standalone render steps:
1. Set the working directory to this `Gale_Synthetic` folder.
2. Make sure `data/survey_synthetic_YYYY.csv` and `data/prior_year_matches_synthetic_YYYY-1.csv` already exist for the year you want.
3. Render with parameters similar to:

```r
rmarkdown::render(
  input = "stable_matching_paper_synthetic.rmd",
  output_file = "Output/stable_matching_2023_u1p100.html",
  params = list(
    year = 2023,
    u = 1.10,
    heavy = FALSE,
    artifacts_dir = "artifacts"
  )
)
```

If the synthetic CSV inputs do not exist yet, run `build_synthetic_inputs.R` or `run_all_synthetic.r` first.

```{r package_function_load, include = FALSE, cache = FALSE, warning = FALSE, message = FALSE}
paper_version <- TRUE
if (!exists("params") || is.null(params$year)) {
  stop("params$year is not set. Did you pass params = list(year = ...) to render?")
}
year <- params$year

# Multiplier by overall_survey_match_num added to cosine_similiarity or word_matching
u <- if (!is.null(params$u)) params$u else 0.25
artifacts_dir <- if (!is.null(params$artifacts_dir)) params$artifacts_dir else "artifacts"

u_tag <- gsub("\\.", "p", sprintf("%.3f", u))   # e.g., 0.175 -> "0p175", 0.150 -> "0p150"
art_dir_u <- file.path(artifacts_dir, paste0("u_", u_tag))
dir.create(art_dir_u, showWarnings = FALSE, recursive = TRUE)

message("Setup: using year = ", year, " and u = ", u)

# Estimated it would take a month to pair.
# Eliminate stopwords
# Previous algorithm: too close in BG or previous mentor
# New table: Show where multiple mentees per mentor
# Feedback: occasional challenge like person no-show or 
# Show where match is the same.
# Note this can easily cause a mentor:mentee match to rank worse, so a pairing does not occur.

## Number of Matching Words
## https://stackverflow.com/a/62031699/2305061
## Seed governs mentor-duplication sampling and the uniform jitter that breaks
## predicted-compatibility ties. Default 88 reproduces the committed artifacts.
run_seed <- if (!is.null(params$seed)) as.integer(params$seed) else 88L
set.seed(run_seed)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.width = 12, fig.height = 8) 


if (require('pacman') == FALSE) {
  stop("Need to install pacman package with install.packages('pacman'), dependencies = TRUE")
}

indir  <- normalizePath('.', winslash = '/', mustWork = TRUE)
data_dir <- file.path(indir, 'data')
outdir <- file.path(indir, 'Output')
dir.create(outdir, showWarnings = FALSE)

pacman::p_load(dplyr, matchingR, openxlsx, textTinyR, stopwords, stringr, rmarkdown,
               tidyr, kableExtra, reactable, ggpubr, tidytext, forcats,
               extrafont, correlation, tibble)

select <- dplyr::select
filter <- dplyr::filter

# No longer needed?
# extrafont::loadfonts(device = "all", quiet = TRUE)

if(!exists('year')) {
  years <- 2023
}

if(!exists('mod_mentee')) {
  mod_mentee <- 0.25
}

jaccard <- function(a, b) {
    intersection = length(intersect(a, b))
    union = length(a) + length(b) - intersection
    return (intersection/union)
}
## Unordered list - https://stackoverflow.com/questions/52335498/convert-list-object-to-unordered-list-in-markdown/52335934#52335934
catList <- function(inputList) {
    cat(gsub("^!omap\n|:", "", yaml::as.yaml(inputList, omap = TRUE)))
}
```

```{r base_1, include = TRUE, echo = TRUE, cache = FALSE, warning = FALSE, message = FALSE}
## Only this file changes
surv_results0 <- readr::read_csv(file.path(data_dir, paste0('survey_synthetic_', year, '.csv')), show_col_types = FALSE)

surv_results0 <- surv_results0[, !grepl("BALLOT", toupper(names(surv_results0)))]

## Print questions <=7 unique responses, many being the multiple choice survey questions
# survey_questions_multiple_choice <- 
#   surv_results0[sapply(surv_results0, function(x) length(unique(x)) <= 7)]
# for(col_name in names(survey_questions_multiple_choice)) {
#   cat("\nQuestion:", col_name, "\n")
#   unique_responses <- unique(survey_questions_multiple_choice[[col_name]])
#   cat("Responses:", paste(unique_responses, collapse = ", "),
#       "\n")
#   readline(prompt = "Press Enter to continue...")
# }

surv_results0 <- janitor::clean_names(surv_results0)
if ("display_name" %in% names(surv_results0)) {
  surv_results0$display_name <- toupper(surv_results0$display_name)
}

is_answered <- function(x) {
  if (is.character(x)) {
    !is.na(x) & nzchar(stringr::str_trim(x))
  } else {
    !is.na(x)
  }
}

mentor_required_fields <- c(
  "what_is_your_grade_level",
  "would_you_prefer_a_mentee_within_your_business_unit_group",
  "what_are_your_strongest_skills_please_choose_your_top_3",
  "what_topics_are_you_knowledgeable_on_please_choose_your_top_3",
  "which_expectations_can_you_help_fulfill_please_choose_your_top_3",
  "do_you_prefer_2_2_or_would_you_be_comfortable_mentoring_more_than_one_person",
  "would_you_consider_yourself_an_extrovert_or_an_introvert",
  "which_personality_type_would_you_prefer_to_be_paired_with",
  "please_tell_us_in_your_own_words_why_you_want_to_be_a_mentor_what_are_your_expectations_and_intended_outcomes_please_provide_a_detailed_response_of_3_4_sentences",
  "affiliation_group",
  "affiliation_unit"
)

mentee_required_fields <- c(
  "what_is_your_grade_level",
  "would_you_prefer_a_mentor_with_your_current_job_role_or_one_above",
  "what_skills_would_you_like_to_improve_please_choose_your_top_3",
  "what_topics_are_you_interested_in_please_choose_your_top_3",
  "what_are_your_expectations_for_this_program_please_choose_your_top_3",
  "would_you_consider_yourself_an_extrovert_or_an_introvert_2",
  "which_personality_type_would_you_prefer_to_be_paired_with_2",
  "please_tell_us_in_your_own_words_why_you_want_to_be_a_mentee_what_are_your_expectations_and_intended_outcomes_please_provide_a_detailed_response_of_3_4_sentences",
  "affiliation_group",
  "affiliation_unit"
)

## This changed at some point between 2022-2025, which number was assigned
##   to column of same name
names(surv_results0) <- gsub("_1", "_2", names(surv_results0))

surv_results_pre_removal <- surv_results0 %>% 
  filter(!grepl("IMPORT", .[[1]], ignore.case = TRUE)) %>% 
  dplyr::filter(!is.na(recipient_last_name) & !is.na(recipient_first_name)) %>% 
  dplyr::filter(!is.na(would_you_like_to_be_a_mentor_or_a_mentee)) %>% 
  mutate(display_name =
    case_when(is.na(display_name) ~ str_trim(
      paste(toupper(first_name), toupper(last_name))),
      TRUE ~ display_name)
    ) %>% 
  group_by(display_name,    
           would_you_like_to_be_a_mentor_or_a_mentee) %>% 
  mutate(free_text_responses_number_of_characters = sum(
           nchar(please_tell_us_in_your_own_words_why_you_want_to_be_a_mentee_what_are_your_expectations_and_intended_outcomes_please_provide_a_detailed_response_of_3_4_sentences),
           nchar(please_tell_us_in_your_own_words_why_you_want_to_be_a_mentor_what_are_your_expectations_and_intended_outcomes_please_provide_a_detailed_response_of_3_4_sentences),
           nchar(are_there_any_special_considerations_that_you_would_like_known_when_your_application_is_reviewed_is_your_desire_to_participate_based_on_certain_criteria_that_you_have_in_mind_that_was_not_covered_in_the_previous_questions_please_list_that_information_here),
           nchar(are_there_any_special_considerations_that_you_would_like_known_when_your_application_is_reviewed_is_your_desire_to_participate_based_on_certain_criteria_that_you_have_in_mind_that_was_not_covered_in_the_previous_questions_please_list_that_information_here_2), 
           na.rm = TRUE)) %>% 
  slice(which.max(free_text_responses_number_of_characters)) %>% 
  mutate(
    mentor_required_complete = dplyr::if_else(
      toupper(would_you_like_to_be_a_mentor_or_a_mentee) == "MENTOR",
      dplyr::if_all(dplyr::all_of(mentor_required_fields), is_answered),
      FALSE
    ),
    mentee_required_complete = dplyr::if_else(
      toupper(would_you_like_to_be_a_mentor_or_a_mentee) == "MENTEE",
      dplyr::if_all(dplyr::all_of(mentee_required_fields), is_answered),
      FALSE
    ),
    required_response_complete = mentor_required_complete | mentee_required_complete
  ) %>%
  ungroup()

# surv_results_pre_removal used in chunk: "Discarded participants' summary (lack of data)" 
surv_results <- surv_results_pre_removal %>% 
  dplyr::filter(required_response_complete) %>% 
  dplyr::filter(toupper(would_you_like_to_be_a_mentor_or_a_mentee) %in% 
                  c('MENTOR','MENTEE')) %>%
  dplyr::select(-mentor_required_complete, -mentee_required_complete)

required_completion_exclusions <- surv_results_pre_removal %>%
  dplyr::filter(toupper(would_you_like_to_be_a_mentor_or_a_mentee) %in% c("MENTOR", "MENTEE")) %>%
  dplyr::transmute(
    year = year,
    role = stringr::str_to_title(would_you_like_to_be_a_mentor_or_a_mentee),
    required_response_complete = required_response_complete
  ) %>%
  dplyr::group_by(year, role) %>%
  dplyr::summarise(
    considered_after_identity_gate = dplyr::n(),
    excluded_required_completion = sum(!required_response_complete, na.rm = TRUE),
    retained_after_completion_gate = sum(required_response_complete, na.rm = TRUE),
    excluded_required_completion_pct = round(
      100 * excluded_required_completion / considered_after_identity_gate,
      1
    ),
    .groups = "drop"
  ) %>%
  dplyr::arrange(role)

## Prior year pairings for repeat-match penalty.
last_year_results <- readr::read_csv(
  file.path(data_dir, paste0('prior_year_matches_synthetic_', year - 1, '.csv')),
  show_col_types = FALSE
) %>% 
  janitor::clean_names() %>% 
  rename(mentor_name = gale_shapley_matched_mentor_name) %>% 
  distinct(mentee_name, mentor_name)

## https://stackoverflow.com/a/65409450/2305061
## Counts unique word matches
numwords <- function(str1, str2) {
  mapply(function(x, y) length(intersect(x, y)), 
         strsplit(str1, ' '), strsplit(str2, ' '))
}

matchwords <- function(str1, str2) {
  mapply(function(x, y) paste0(intersect(x, y),collapse = " "), 
         strsplit(str1, ' '), strsplit(str2, ' '))
}

## checking for best de-duplication when mentor/mentee submits > 1
more_1_submissions_surv_results <- surv_results %>% 
  group_by(display_name, would_you_like_to_be_a_mentor_or_a_mentee) %>% 
  add_count() %>% 
  dplyr::filter(n > 1) %>% 
  janitor::clean_names()
# affiliation_group is intentionally excluded from concatenated text -- Paper 1's
# concat_cols has no org field; affiliation_group feeds only BG_mentor/BG_mentee
# (prefer_mentee_same_BG), computed separately below from surv_results_logical.
surv_results_concat <- surv_results %>%
  select(
    display_name,
    mentor_or_mentee = would_you_like_to_be_a_mentor_or_a_mentee,
    what_are_your_strongest_skills_please_choose_your_top_3,
    what_topics_are_you_knowledgeable_on_please_choose_your_top_3,
    which_expectations_can_you_help_fulfill_please_choose_your_top_3,
    please_tell_us_in_your_own_words_why_you_want_to_be_a_mentor_what_are_your_expectations_and_intended_outcomes_please_provide_a_detailed_response_of_3_4_sentences,
    are_there_any_special_considerations_that_you_would_like_known_when_your_application_is_reviewed_is_your_desire_to_participate_based_on_certain_criteria_that_you_have_in_mind_that_was_not_covered_in_the_previous_questions_please_list_that_information_here,
    what_skills_would_you_like_to_improve_please_choose_your_top_3,
    what_topics_are_you_interested_in_please_choose_your_top_3,
    what_are_your_expectations_for_this_program_please_choose_your_top_3,
    please_tell_us_in_your_own_words_why_you_want_to_be_a_mentee_what_are_your_expectations_and_intended_outcomes_please_provide_a_detailed_response_of_3_4_sentences,
    are_there_any_special_considerations_that_you_would_like_known_when_your_application_is_reviewed_is_your_desire_to_participate_based_on_certain_criteria_that_you_have_in_mind_that_was_not_covered_in_the_previous_questions_please_list_that_information_here_2
  )

surv_results_concat_skills_improve <- surv_results_concat %>% 
  rename(
    mentor_skills_offer = what_are_your_strongest_skills_please_choose_your_top_3,
    mentee_skills_improve = what_skills_would_you_like_to_improve_please_choose_your_top_3
  ) %>% 
  select(mentor_skills_offer, mentee_skills_improve,
         display_name, mentor_or_mentee)

surv_results_concat_skills_improve_mentor <-
  surv_results_concat_skills_improve %>% 
  dplyr::filter(mentor_or_mentee == "Mentor") %>% 
  rename(Mentor.Name = display_name) %>% 
  select(Mentor.Name, mentor_skills_offer) %>% 
  mutate(dummy = 1)

surv_results_concat_skills_improve_mentee <-
  surv_results_concat_skills_improve %>% 
  dplyr::filter(mentor_or_mentee == "Mentee") %>% 
  rename(Mentee.Name = display_name) %>% 
  select(Mentee.Name, mentee_skills_improve) %>% 
  mutate(dummy = 1)

## Used only in mentee-specific adjustment - 4pivot_mentee data frames
surv_results_concat_skills_improve_mentor_Matching_Words <- 
  full_join(surv_results_concat_skills_improve_mentor,
            surv_results_concat_skills_improve_mentee,
            multiple = 'all') %>% 
  mutate(
    mentor_skills_match =
             numwords(
                        str_replace_all(
                         str_replace_all(toupper(mentor_skills_offer), "[:space:]+", ""),
                         "[,]",
                         " "),
                        str_replace_all(
                         str_replace_all(toupper(mentee_skills_improve), "[:space:]+", ""),
                         "[,]",
                         " ")
             )
  ) %>% 
  select(Mentor.Name, Mentee.Name, mentor_skills_match)

more_1_submissions_surv_results_concat <- 
  inner_join(surv_results_concat,
             more_1_submissions_surv_results %>% 
               distinct(display_name,    
                        would_you_like_to_be_a_mentor_or_a_mentee)
             )

if (nrow(more_1_submissions_surv_results_concat) > 0) {
  # Legacy duplicate-submission completeness diagnostics intentionally disabled.
  # Repaired reference version kept below for future reactivation if needed.
  # more_1_submissions_surv_results_concat_mentor <-
  #   more_1_submissions_surv_results_concat %>%
  #   dplyr::filter(would_you_like_to_be_a_mentor_or_a_mentee == "Mentor")
  # more_1_submissions_surv_results_concat_mentee <-
  #   more_1_submissions_surv_results_concat %>%
  #   dplyr::filter(would_you_like_to_be_a_mentor_or_a_mentee == "Mentee")
  #
  # mentor_complete_cols <- colSums(is.na(more_1_submissions_surv_results_concat_mentor)) == 0
  # mentee_complete_cols <- colSums(is.na(more_1_submissions_surv_results_concat_mentee)) == 0
  # more_1_submissions_surv_results_concat_mentor <-
  #   more_1_submissions_surv_results_concat_mentor[, mentor_complete_cols, drop = FALSE]
  # more_1_submissions_surv_results_concat_mentee <-
  #   more_1_submissions_surv_results_concat_mentee[, mentee_complete_cols, drop = FALSE]
  #
  # max_chars_more_1_submissions_surv_results0 <-
  #   apply(
  #     X = more_1_submissions_surv_results_concat_mentor,
  #     MARGIN = 2,
  #     FUN = function(x) max(nchar(as.character(x)), na.rm = TRUE)
  #   )
  more_1_submissions_surv_results_concat_mentor <- data.frame()
  more_1_submissions_surv_results_concat_mentee <- data.frame()
  max_chars_more_1_submissions_surv_results0    <- data.frame()
} else {
  more_1_submissions_surv_results_concat_mentor <- data.frame()
  more_1_submissions_surv_results_concat_mentee <- data.frame()
  max_chars_more_1_submissions_surv_results0    <- data.frame()
}

surv_results_logical <- surv_results %>% 
  rename(
    mentor_or_mentee = would_you_like_to_be_a_mentor_or_a_mentee,
    grade = what_is_your_grade_level,
    prefer_mentee_same_BG = would_you_prefer_a_mentee_within_your_business_unit_group,
    extra_intro_mentor = would_you_consider_yourself_an_extrovert_or_an_introvert,
    extra_intro_mentee = would_you_consider_yourself_an_extrovert_or_an_introvert_2,
    personality_pair_mentor = which_personality_type_would_you_prefer_to_be_paired_with,
    mentor_above_role = would_you_prefer_a_mentor_with_your_current_job_role_or_one_above,
    personality_pair_mentee = which_personality_type_would_you_prefer_to_be_paired_with_2
  ) %>% 
  select(display_name, mentor_or_mentee, 
         extra_intro_mentee, extra_intro_mentor,
         personality_pair_mentor, personality_pair_mentee,
         mentor_above_role,
         grade, prefer_mentee_same_BG,
         affiliation_group) 

surv_results_logical_mentor <- surv_results_logical %>% 
  dplyr::filter(mentor_or_mentee == "Mentor") %>% 
  rename(Mentor.Name = display_name,
         grade_mentor = grade,
         BG_mentor = affiliation_group) %>% 
  select(Mentor.Name, extra_intro_mentor, 
         grade_mentor, 
         prefer_mentee_same_BG,
         personality_pair_mentor, BG_mentor) 

surv_results_logical_mentee <- surv_results_logical %>% 
  dplyr::filter(mentor_or_mentee == "Mentee") %>% 
  rename(Mentee.Name = display_name,
         grade_mentee = grade,
         BG_mentee = affiliation_group) %>% 
  select(Mentee.Name, mentor_above_role,
         extra_intro_mentee, 
         grade_mentee, 
         personality_pair_mentee, BG_mentee)

multiple_mentee_mentors0 <- surv_results %>% 
  select(
    display_name,
    mentor_or_mentee = would_you_like_to_be_a_mentor_or_a_mentee,
    more_1_mentee = do_you_prefer_2_2_or_would_you_be_comfortable_mentoring_more_than_one_person
  ) %>% 
  dplyr::filter(mentor_or_mentee == "Mentor") %>% 
  dplyr::filter(!more_1_mentee %in% c('1 mentee',"",NA)) %>% 
  rename(Mentor.Name = display_name)

multiple_mentee_mentors <- multiple_mentee_mentors0 %>% 
  select(-2)

# Legacy capacity summary retained as a repaired comment only; unused downstream.
# multiple_mentee_mentors_max <- if (nrow(multiple_mentee_mentors) == 0) {
#   1
# } else {
#   max(
#     as.numeric(str_extract(multiple_mentee_mentors$more_1_mentee, "\\d+")),
#     na.rm = TRUE
#   )
# }

concat_cols <- setdiff(colnames(surv_results_concat),
                       c("display_name","mentor_or_mentee"))

concat_cols_freetext_only <- c("a")

mentor_in0_prep <- surv_results_concat %>% 
  dplyr::filter(mentor_or_mentee == "Mentor") %>% 
  select(-2)

mentor_in0 <- mentor_in0_prep %>% 
  tidyr::unite("mentor_concatenated_responses", all_of(concat_cols), sep = " ", na.rm = TRUE) %>% 
  mutate(
    mentor_concatenated_responses = 
      str_replace_all(mentor_concatenated_responses, "[-,/]", " "),           
    mentor_concatenated_responses = 
      str_replace_all(
        str_replace_all(toupper(mentor_concatenated_responses), "[^A-Z /]", " "),
                         "[:space:]+",
                         " "),
    mentor_concatenated_responses = 
      str_replace_all(mentor_concatenated_responses," NA ", ""))

mentor_in_base <- mentor_in0 %>%
  mutate_if(is.character, str_trim) %>%
  rename(Mentor.Name = display_name)
##### Mentee ----
mentee_in0_prep <- surv_results_concat %>% 
  dplyr::filter(mentor_or_mentee == "Mentee") %>% 
  select(-2)

mentee_in0 <- mentee_in0_prep %>% 
  tidyr::unite("mentee_concatenated_responses", all_of(concat_cols), sep = " ", na.rm = TRUE) %>% 
  mutate(
    mentee_concatenated_responses = 
      str_replace_all(mentee_concatenated_responses, "[-,/]", " "),           
    mentee_concatenated_responses = 
      str_replace_all(
        str_replace_all(toupper(mentee_concatenated_responses), "[^A-Z /]", " "),
                         "[:space:]+",
                         " "),
    mentee_concatenated_responses = 
      str_replace_all(mentee_concatenated_responses," NA ", ""))

mentee_in1 <- left_join(mentee_in0, last_year_results %>% 
                          distinct(mentee_name, mentor_name),
                        by = c('display_name' = 'mentee_name'))

mentee_in_base <- mentee_in1 %>%
  rename(Matched_mentor_last_year = mentor_name,
                       Mentee.Name = display_name) %>%
  mutate_if(is.character, str_trim)

mentor_starter_rows <- nrow(mentor_in_base)
mentor_multiple_mentee_rows <- nrow(multiple_mentee_mentors)
mentee_starter_rows <- nrow(mentee_in_base)

## Mentor:Mentee imbalance resolution ----

if (mentor_starter_rows > mentee_starter_rows) {
  ## if more mentors than mentees, no change and allowing Gale-Shapley to leave some unmatched
  mentee_in          <- mentee_in_base
  mentor_in          <- mentor_in_base
} else if (mentee_starter_rows > mentor_starter_rows) {
#### Multiple mentees ----
  ## if more mentees than mentors, duplicate mentors who indicates willingness to take 2 mentees
  mentee_in          <- mentee_in_base
  
  add_row_counter    <- mentee_starter_rows - mentor_starter_rows
  random_mentors     <- round(runif(add_row_counter, 1, mentor_multiple_mentee_rows))
  
  ## shuffle multiple mentee dataframe randomly
  multiple_mentee_mentors_shuffled <- multiple_mentee_mentors[
    sample(seq_len(nrow(multiple_mentee_mentors))), ]
  multiple_mentee_mentors_shuffled_full_mentor_data <- 
    inner_join(mentor_in_base,
               multiple_mentee_mentors_shuffled %>% 
                 distinct(Mentor.Name))
    
  ## now make enough rows given number of mentees, without causing any mentor
  ## to repeat unless necessary
  mentor_in          <- mentor_in_base
  needed_rows <- mentee_starter_rows - nrow(mentor_in)
  while (needed_rows > 0) {
    ## print(paste("Needed rows for mentor count to equal mentee count: ", needed_rows))
    ## Below, the scores used for ranking get modified 
    ##   look for str_sub(Mentor.Name, -1) == '2' ~ CS_Pred_compatibility - 0.5,
    ## Legacy helper retained as a comment only; it was not used by the loop.
    ## rows_available <- nrow(multiple_mentee_mentors_shuffled_full_mentor_data) - needed_rows
    mentor_in <-
      bind_rows(mentor_in,
                multiple_mentee_mentors_shuffled_full_mentor_data %>% 
                  slice(1:needed_rows))
    needed_rows <- mentee_starter_rows - nrow(mentor_in)
    
  }
} else {
  mentee_in          <- mentee_in_base
  mentor_in          <- mentor_in_base
}

mentor_in <- mentor_in %>% 
  group_by(Mentor.Name, mentor_concatenated_responses) %>% 
  mutate(num_mentees = n()) %>% 
  ungroup() %>% 
  mutate(mentor_id = row_number()) %>% 
  distinct(Mentor.Name, mentor_concatenated_responses, mentor_id, num_mentees)

mentee_in <- mentee_in %>% 
  mutate(mentee_id = row_number())

## Potenial future use if need NA fill
# gfg_data<- data.frame(col1 = c(OCC1,rep(NA, max_ln - length(OCC1))),
#                       col2 = c(OCC2,rep(NA, max_ln - length(OCC2))))

## https://community.rstudio.com/t/similarity-between-sents-in-two-columns/141509
max_ln <- max(
  length(mentor_in$mentor_concatenated_responses),
  length(mentee_in$mentee_concatenated_responses)
)
```


```{r show_setup2, include = TRUE, echo = TRUE, cache = FALSE}
## !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!! ##
##     to evaluate stopwords used by tidytext, same source is snowball
## english_stopwords <- toupper(stopwords::stopwords(source = 'snowball')) 
## !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!! ##

## 1 row per word - MANY rows
mentor_concatenated_responses_unnest <- mentor_in %>% 
  select(mentor_id, mentor_concatenated_responses) %>% 
  unnest_tokens(word, mentor_concatenated_responses) %>% 
  select(mentor_id, word)

mentor_concatenated_responses_unnest_no_stopwords <- 
  mentor_concatenated_responses_unnest %>% 
    # get_stopwords() default is snowball
    anti_join(get_stopwords(source = "snowball")) %>% 
    dplyr::filter(nchar(word) >= 2) %>% 
    dplyr::filter(!word %in% c('im','id', 'go', 'bg'))

## Evaluate what terms to remove from mentor_concatenated_responses_unnest above
# mentor_concatenated_responses_unnest_no_stopwords %>%
#   dplyr::filter(nchar(word) < 3) %>%
#   janitor::tabyl(word) %>%
#   arrange(desc(n))

mentor_concatenated_responses_no_stopwords_frm <- mentor_concatenated_responses_unnest_no_stopwords %>% 
  group_by(mentor_id) %>% 
  summarize(mentor_concatenated_responses_no_stopwords = toupper(paste(word, collapse = " "))) %>% 
  ungroup() %>% 
  select(mentor_id, mentor_concatenated_responses_no_stopwords)

mentor_in <- mentor_in %>% 
  left_join(., mentor_concatenated_responses_no_stopwords_frm,
            multiple = "all")

## 1 row per word - MANY rows
mentee_concatenated_responses_unnest <- mentee_in %>% 
  unnest_tokens(word, mentee_concatenated_responses) %>% 
  select(mentee_id, word)

mentee_concatenated_responses_unnest_no_stopwords <- 
  mentee_concatenated_responses_unnest %>% 
    anti_join(get_stopwords(source = "snowball")) %>% 
    dplyr::filter(nchar(word) >= 2)

mentee_concatenated_responses_no_stopwords_frm <- mentee_concatenated_responses_unnest_no_stopwords %>% 
  group_by(mentee_id) %>% 
  summarize(mentee_concatenated_responses_no_stopwords = toupper(paste(word, collapse = " "))) %>% 
  ungroup() %>% 
  select(mentee_id, mentee_concatenated_responses_no_stopwords)

mentee_in <- mentee_in %>% 
  ## Multiple mentees may exist because of duplicates for 
  ## mentor:mentee imbalance in 
  left_join(., mentee_concatenated_responses_no_stopwords_frm,
            multiple = "all")

all_data <- data.frame(
  col1 = c(unique(mentor_in$mentor_concatenated_responses_no_stopwords),
           rep(NA, max_ln - length(unique(mentor_in$mentor_concatenated_responses_no_stopwords)))),
  col2 = c(unique(mentee_in$mentee_concatenated_responses_no_stopwords),
           rep(NA, max_ln - length(unique(mentee_in$mentee_concatenated_responses_no_stopwords))))
)

all_combinations <-
  expand.grid(unique(all_data$col1),
              unique(all_data$col2), stringsAsFactors = FALSE)
all_combinations <- all_combinations %>% 
  dplyr::filter(!is.na(Var1) & !is.na(Var2))
```

```{r matching_score_derivation, include = TRUE, echo = TRUE, cache = FALSE}
alignment_combinations_base0 <- all_combinations %>%
  mutate(Cosine_Similarity =
           COS_TEXT(text_vector1 =
                      str_replace_all(
                       str_replace_all(toupper(Var1), "[^A-Z ]", ""),
                       "[:space:]+",
                       " "),
                    text_vector2 =
                      str_replace_all(
                       str_replace_all(toupper(Var2), "[^A-Z ]", ""),
                       "[:space:]+",
                       " ")
           ),
         MW_count =
           numwords(
                      str_replace_all(
                       str_replace_all(toupper(Var1), "[^A-Z ]", ""),
                       "[:space:]+",
                       " "),
                   
                      str_replace_all(
                       str_replace_all(toupper(Var2), "[^A-Z ]", ""),
                       "[:space:]+",
                       " ")
           ),
         Matching_Words = 
           matchwords(
                      str_replace_all(
                       str_replace_all(toupper(Var1), "[^A-Z ]", ""),
                       "[:space:]+",
                       " "),
                      str_replace_all(
                       str_replace_all(toupper(Var2), "[^A-Z ]", ""),
                       "[:space:]+",
                       " ")
           )
  )

last_year_results_with_id <-
  ## acquire mentor_id
  left_join(last_year_results,
            mentor_in %>% distinct(Mentor.Name, mentor_id,
                                   mentor_concatenated_responses_no_stopwords),
            by = c('mentor_name' = 'Mentor.Name'),
            ## duplication of mentors to balance mentor:mentee count 
            ## can cause many:1 join
            multiple = "all") %>% 
  ## acquire mentee_id
  left_join(.,
            mentee_in %>% distinct(Mentee.Name, mentee_id,
                                   mentee_concatenated_responses_no_stopwords),
            by = c('mentee_name' = 'Mentee.Name'),
            ## duplication of mentors to balance mentor:mentee count 
            ## can cause many:1 join
            multiple = "all") %>% 
  distinct(mentor_name, mentee_name, .keep_all = TRUE) %>% 
  mutate (
   Matching_Words = 
           matchwords(
                      str_replace_all(
                       str_replace_all(toupper(mentor_concatenated_responses_no_stopwords), "[^A-Z ]", ""),
                       "[:space:]+",
                       " "),
                      str_replace_all(
                       str_replace_all(toupper(mentee_concatenated_responses_no_stopwords), "[^A-Z ]", ""),
                       "[:space:]+",
                       " ")
           )
   ) 

#### Base Variable Assignment ----
## Implement loop-indicated multipliers ID'd in other scripts
## Top words in original matches

## Mentor has extra/introvert preference and mentee matches
a <-  5
# Mentor has no extra/intro preference
b <-  -5
# All other mentor extra/intro possibilities
pers_other_mentor <- -15
## Mentee has extra/introvert preference and mentor matches
d <-  25
# Mentee extra/introvert preference matches how mentor identified
e <-  5
# Mentee has no extra/introvert preference
f <-  0
# All other mentee extra/intro possibilities
g <- -10
### grade_subscore

## h + 25 if mentee prefers higher grade mentor, mentee grade is 1, mentor 1-4 grades above mentee
#  h + 20 if mentee prefers higher grade mentor, mentee grade is 1-3, mentor 1-2 grades above mentee
#  h + 15 if mentee prefers higher grade mentor, mentee grade is 4+, mentor 1-2 grades above mentee
#  h + 5 if mentee prefers higher grade mentor and mentor 1 grade above mentee
#  h + 0 if mentee prefers higher grade mentor
h <-  100
## If no h condition met, then :
# i + 5 if mentee wanted a mentor of the same grade, mentee grade is 5+, mentor/mentee same grade
# i if mentee wanted a mentor of the same grade, mentee grade is 3+, mentor/mentee same grade
i <-  90
## If no h or i condition met, then:
# j + 0 if mentor grade is above mentee
j <-  60
## If no h, i, j condition met, then:
# k + 0 if mentor/mentee same grade
k <-  5
## If no h, i, j, k condition met, then:
# l + 0 if mentor grade LESS than mentee
l <-  -100
### BG_match
# m + 0 if mentee prefers a mentor of the same BG and mentor/mentee same BG
m <-  10
# n + 0 if mentee prefers a mentor of a different BG and mentor/mentee different BG
n <-  0
# o + 0 if mentee has no preference about mentor BG
o <-  0
# All other BG preference comparisons
p <- -10
# multiplier for mentor_skills_match
q <- 20
# multiplier of # of words extracted from the columns in concat_cols that match between the mentor and mentee responses
# !!! Ignored in this script because operates on some consideration of 2022 Matching Words - dropped.
word_match_multiplier <-  1
# !!! u SET AT TOP !!!
# Multiplier by overall_survey_match_num added to cosine_similiarity or word_matching
# u <- SET AT TOP
# !!! u SET AT TOP !!!

## although used a = 16 in May, 2023 so just one match with lower grade mentor
#   a2 b2 c2 d2 e2 f2  g2  h2  i2 j2 k2 l2 m2 n2 o2 p2 q2 r2 s2 t2   u2  cor_original_match_words_cos cor_original_match_words_matchct
# 1 18  0 -5  2  2  0 -10 110 100 80 85  0  2  2  1 -5  3  3  2  1 0.25 0.5155368 0.6160533

################### SPECIAL NOTE ############################
## It is not helpful to use V in terms of the correlations ##
## so not using here but am using for                      ##
## mentee-specific adjustment - 4pivot_mentee data frames  ##
## ##########################################################

## Dropped use of original_match_count_of_top_Matching_Words
alignment_combinations_base <- 
  alignment_combinations_base0

mentor_mentee_alignment0 <- 
    left_join(mentor_in, alignment_combinations_base,
              by = c('mentor_concatenated_responses_no_stopwords' = 'Var1'),
              multiple = 'all') %>%
    left_join(., mentee_in %>% distinct(mentee_id, Mentee.Name, 
                                        Matched_mentor_last_year,
                                        mentee_concatenated_responses_no_stopwords),
              by = c('Var2' = 'mentee_concatenated_responses_no_stopwords'),
              multiple = 'all') %>% 
    ## Acquires mentor_skills_match
    left_join(., surv_results_concat_skills_improve_mentor_Matching_Words) %>% 
    mutate(mentor_skills_match = q *  mentor_skills_match) %>% 
    rename(mentee_concatenated_responses_no_stopwords = Var2) %>% 
    distinct(mentor_id, mentee_id, .keep_all = TRUE)

surv_results_logical_remove <- setdiff(
  c(colnames(surv_results_logical_mentor),
    colnames(surv_results_logical_mentee)),
  c("Mentee.Name","Mentor.Name"))

mentor_mentee_alignment_allvars0 <- 
  left_join(mentor_mentee_alignment0, surv_results_logical_mentor) %>% 
  left_join(., surv_results_logical_mentee) %>% 
  mutate(grade_mentor_num = 
           as.numeric(
             str_extract(grade_mentor, "\\d+")),
         grade_mentee_num = 
           as.numeric(
             str_extract(grade_mentee, "\\d+"))) %>% 
  left_join(., surv_results %>% 
                  dplyr::filter(would_you_like_to_be_a_mentor_or_a_mentee == 'Mentor') %>% 
                  rename(Mentor.Name = display_name) %>% 
                  distinct(Mentor.Name, free_text_responses_number_of_characters, corp_id) %>% 
                  rename(Mentor_free_text_responses_number_of_characters = 
                            free_text_responses_number_of_characters,
                         Mentor_corp_id = corp_id)
            ) %>% 
  left_join(., surv_results %>% 
                  dplyr::filter(would_you_like_to_be_a_mentor_or_a_mentee == 'Mentee') %>% 
                  rename(Mentee.Name = display_name) %>% 
                  distinct(Mentee.Name, free_text_responses_number_of_characters, corp_id) %>% 
                  rename(Mentee_free_text_responses_number_of_characters = 
                            free_text_responses_number_of_characters,
                         Mentee_corp_id = corp_id)
            )

#### Weights ----
mentor_mentee_alignment_allvars <- mentor_mentee_alignment_allvars0 %>% 
  mutate(personality_mentee_match = case_when(
           personality_pair_mentor == extra_intro_mentee ~ a,
           personality_pair_mentor == "No preference" ~ b,
           TRUE ~ pers_other_mentor),
         personality_mentor_match = case_when(
           personality_pair_mentee == extra_intro_mentor ~ d,
           personality_pair_mentee == personality_pair_mentor ~ e,
           personality_pair_mentee == "No preference" ~ f,
           TRUE ~ g),
         ####################################################
         ##!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!##
         ##  Relative mentor:mentee grade solution was     ##
         ##  achieved after much experimentation, yiedling ##
         ##  no concerning grade:grade mentor:mentee       ##
         ##  matches after Gale-Shapley does its work to   ##
         ##  pair, both for Cosine Similarity and Word     ##
         ##  Matching                                      ##
         ##!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!##
         ####################################################
         grade_mentor_minus_mentee = grade_mentor_num - grade_mentee_num,
         grade_subscore = case_when(
           mentor_above_role == "Above" & grade_mentee_num <= 1 & grade_mentor_minus_mentee <= 4 &  
             grade_mentor_num > grade_mentee_num ~ h + 25,
           mentor_above_role == "Above" & grade_mentee_num <= 3 & grade_mentor_minus_mentee <= 2 & 
             grade_mentor_num > grade_mentee_num ~ h + 20,
           mentor_above_role == "Above" & grade_mentee_num > 3 & grade_mentor_minus_mentee <= 2 & 
             grade_mentor_num > grade_mentee_num ~ h + 15,
           mentor_above_role == "Above" & grade_mentor_minus_mentee <= 1 &
             grade_mentor_num > grade_mentee_num ~ h + 5,
           mentor_above_role == "Above" & 
             grade_mentor_num > grade_mentee_num ~ h,
           mentor_above_role == "Same role/function" & grade_mentee_num >= 5 &
             grade_mentor_num == grade_mentee_num ~ (i + 5),
           mentor_above_role == "Same role/function" & grade_mentee_num >= 3 &
             grade_mentor_num == grade_mentee_num ~ i,
           ## Need same grade to be higher weight to avoid high >5% paired with mentor of lower grade
           grade_mentor_num > grade_mentee_num ~ j,
           grade_mentor_num == grade_mentee_num ~ k,
           grade_mentor_num < grade_mentee_num ~ l),
         BG_match = case_when(
           prefer_mentee_same_BG == "Yes" & 
             BG_mentee == BG_mentor ~ m,
           prefer_mentee_same_BG == "No" & 
             BG_mentee != BG_mentor ~ n,
           prefer_mentee_same_BG == "No preference" ~ o,
           TRUE ~ p),
         ## Removed by program-owner decision, 2023-04-20.
         # prefer_interaction_type_num = case_when(
         #   (prefer_interaction_type_mentor == "No preference" |
         #    prefer_interaction_type_mentee == "No preference") ~ q,
         #   prefer_interaction_type_mentee == prefer_interaction_type_mentor ~ r,
         #   TRUE ~ s),
         mentor_concatenated_responses_chars = nchar(mentor_concatenated_responses_no_stopwords),
         mentee_concatenated_responses_chars = nchar(mentee_concatenated_responses_no_stopwords),
         ## Did not help
         concatenated_responses_num_mentor_minus_mentee = 
           100 - (abs(mentor_concatenated_responses_chars - mentee_concatenated_responses_chars))
         ) %>% 
  group_by(mentor_id, mentee_id) %>% 
  mutate(overall_survey_match_num = sum(
                                personality_mentee_match, 
                                personality_mentor_match,
                                grade_subscore,         
                                BG_match,
                                mentor_skills_match
                                ## Removed by program-owner decision, 2023-04-20.
                                ## prefer_interaction_type_num
                                ))

mentor_mentee_alignment <- mentor_mentee_alignment_allvars %>% 
  # select(-personality_mentee_match, -personality_mentor_match,
  #        -grade_subscore, -BG_match,
  #        -prefer_interaction_type_num) %>% 
  select(-all_of(surv_results_logical_remove))

## ── Synthetic-repo deviation from the published paper ────────────────────────
## Pack et al. (2026) use raw scaling:
##   CS_Pred = (Cosine_Similarity * 100) + u * overall_survey_match_num
##   MW_Pred =  MW_count                 + u * overall_survey_match_num
##
## This repository replaces the ad-hoc *100 with z-score normalisation:
##   CS_Pred = z(Cosine_Similarity) + u * z(overall_survey_match_num)
##   MW_Pred = z(MW_count)          + u * z(overall_survey_match_num)
##
## Motivation: even after the overflow-token fix, the survey-match component
## (driven by the grade weights h=100..125) has ~11x more SD than
## Cosine_Similarity*100. Z-scoring makes u the explicit relative-weight
## parameter: u=1.5 means the survey term gets 1.5x the leverage of the NLP
## term, not ~11x. Rankings and headline figures will differ from the paper.
## See README "Deviations from the published paper".

## Guard: if all values in a column are identical, scale() returns NaN (SD=0).
## Return a zero vector so downstream sorting is deterministic rather than crashing.
scale_safe <- function(x) {
  z <- scale(x)[, 1]
  if (all(is.nan(z))) rep(0, length(z)) else z
}

mentor_mentee_alignment <- mentor_mentee_alignment %>%
  ungroup() %>%
  mutate(
    CS_Pred_compatibility =
      scale_safe(Cosine_Similarity) + (u * scale_safe(overall_survey_match_num)),
    MW_Pred_compatibility =
      scale_safe(MW_count)          + (u * scale_safe(overall_survey_match_num))
  )
# End of Weights section
####

mentor_mentee_rowct <- nrow(mentor_mentee_alignment)

## Random alteration to ensure no duplicates of rank, such as if 
## a mentor has more than 1 mentee and was therefore duplicated above.
mentor_mentee_alignment$CS_Pred_compatibility <-
  mentor_mentee_alignment$CS_Pred_compatibility +
  runif(mentor_mentee_rowct, 0.000001, 0.000009)
mentor_mentee_alignment$MW_Pred_compatibility <-
  mentor_mentee_alignment$MW_Pred_compatibility +
  runif(mentor_mentee_rowct, 0.000001, 0.000009)

## Confirm no duplicates so each mentor / mentee pair has unique weight in Gale Shapley
## mentor_mentee_alignment %>% group_by(CS_Pred_compatibility) %>% summarise(ct = n()) %>% arrange(desc(ct)) %>% slice(1:5)

####
#      i    j cor_original_match_words_cos cor_original_match_words_matchct cor_original_match_words_hybrid
# 1 0.25 0.25                    0.4577827                        0.4394523                        0.480596
# > print(stat_frm_optimal_mod_original_match_words %>% 
# +           dplyr::filter(cor_original_match_words_matchct ==
# +                             max(cor_original_match_words_matchct))
# + )
#      i   j cor_original_match_words_cos cor_original_match_words_matchct cor_original_match_words_hybrid
# 1 0.75 1.5                    0.4343059                        0.5349214                       0.5177624
# > print(stat_frm_optimal_mod_original_match_words %>% 
# +           dplyr::filter(cor_original_match_words_hybrid ==
# +                             max(cor_original_match_words_hybrid))
# + )
#      i    j cor_original_match_words_cos cor_original_match_words_matchct cor_original_match_words_hybrid
# 1 0.25 0.75     
```

```{r show_setup3_gale_shapley_pairings, include = TRUE, echo = TRUE}
## more columns in this one for mentor_mentee_alignment_rank_cos_sim_4pivot
mentor_mentee_alignment_rank_cos_sim_4pivot_mentee <-
  left_join(
    mentor_mentee_alignment,
    mentor_mentee_alignment_allvars %>% 
              distinct(Mentor.Name, grade_mentor, 
                       Mentee.Name, grade_mentee, num_mentees,
                       mentor_above_role)) %>% 
  # mutate(
  #   CS_Pred_compatibility_mentee = 
  #     CS_Pred_compatibility + (personality_mentor_match * mod_mentee)
  #   ) %>% 
  mutate(
    CS_Pred_compatibility_mentee =
      CS_Pred_compatibility
    ) %>%
  group_by(mentee_id) %>%
    mutate(GS_mentee_rank_of_mentor = row_number(desc(CS_Pred_compatibility_mentee))) %>%
  ungroup() %>%
  select(mentor_id, mentee_id, 
         grade_mentor, grade_mentee,
         GS_mentee_rank_of_mentor, 
         CS_Pred_compatibility_mentee)

mentor_mentee_alignment_rank_cos_sim_4pivot_mentor <-
  left_join(
    mentor_mentee_alignment,
    mentor_mentee_alignment_allvars %>% 
              distinct(Mentor.Name, grade_mentor,
                       Mentee.Name, grade_mentee, num_mentees)) %>% 
  group_by(mentor_id) %>%
  mutate(GS_mentor_rank_of_mentee = row_number(desc(CS_Pred_compatibility))) %>%
  ungroup() %>%
  select(mentor_id, mentee_id, 
         GS_mentor_rank_of_mentee, CS_Pred_compatibility, 
         num_mentees)

mentor_mentee_alignment_rank_cos_sim_4pivot <- 
  inner_join(mentor_mentee_alignment_rank_cos_sim_4pivot_mentee,
             mentor_mentee_alignment_rank_cos_sim_4pivot_mentor)

mentor_mentee_alignment_rank_cos_sim <- 
  mentor_mentee_alignment_rank_cos_sim_4pivot %>% 
  select(-CS_Pred_compatibility, -CS_Pred_compatibility_mentee,
         -num_mentees)

mentor_with_alignment_pivot_cos_sim <-
  mentor_mentee_alignment_rank_cos_sim_4pivot %>%
  pivot_wider(id_cols = mentor_id, names_from = mentee_id,
              values_from = CS_Pred_compatibility)

mentor_with_alignment_pivot_num_mentees_cos_sim <-
  mentor_mentee_alignment_rank_cos_sim_4pivot %>%
  distinct(mentor_id, num_mentees)

num_mentees_slot_cos_sim <- 
  mentor_with_alignment_pivot_num_mentees_cos_sim %>% 
    mutate(num_mentees = as.double(num_mentees)) %>% 
    pull(num_mentees)

mentee_with_alignment_pivot_cos_sim <-
  mentor_mentee_alignment_rank_cos_sim_4pivot %>%
  pivot_wider(id_cols = mentee_id, names_from = mentor_id,
              values_from = CS_Pred_compatibility_mentee)

matching_cos_sim <- galeShapley.marriageMarket(
  mentee_with_alignment_pivot_cos_sim %>% select(-mentee_id),
  mentor_with_alignment_pivot_cos_sim %>% select(-mentor_id)
  )

match_cos_sim_frm <- data.frame(matching_cos_sim$engagements)

colnames(match_cos_sim_frm) <- 'engagements'

match_frm_more_cols_cos_sim <- match_cos_sim_frm %>%
      mutate(mentee_id = row_number(),
             mentor_id = engagements) %>%
  select(-engagements) %>%
  left_join(.,
            mentor_in %>% select(mentor_id, Mentor.Name)) %>%
  left_join(.,
            mentee_in %>% select(mentee_id, Mentee.Name,  
                                Matched_mentor_last_year)) %>% 
  arrange(Mentee.Name) %>%
  mutate(Algorithm_Same_Match = case_when(
      Mentor.Name == Matched_mentor_last_year ~ TRUE,
      TRUE ~ FALSE)) %>%
  relocate(Mentee.Name, Mentor.Name, Matched_mentor_last_year, Algorithm_Same_Match)

match_distribute_frm_cos_sim <- match_frm_more_cols_cos_sim %>%
  select(Mentee.Name, Mentor.Name, Matched_mentor_last_year, Algorithm_Same_Match) %>%
  rename(GaleShapley_Matched_Mentor_Name = Mentor.Name)

match_full_stat_frm_cos_sim <-
  left_join(match_frm_more_cols_cos_sim, mentor_mentee_alignment_rank_cos_sim) %>%
  left_join(., mentor_mentee_alignment_allvars0 %>% 
                distinct(Mentor.Name, Mentee.Name,
                         Mentor_corp_id, Mentee_corp_id,
                         grade_mentor, grade_mentee)) %>% 
  dplyr::filter(!is.na(Mentor.Name) & !is.na(Mentee.Name)) %>% 
  rename(GaleShapley_Matched_Mentor_Name = Mentor.Name) %>%
  select(-mentor_id, -mentee_id) %>% 
  relocate(all_of(
    c("grade_mentor", 
      "grade_mentee")),
    .after = "GS_mentee_rank_of_mentor") %>% 
  select(
    Mentee.Name, GaleShapley_Matched_Mentor_Name,
    grade_mentee, grade_mentor,
    GS_mentee_rank_of_mentor, GS_mentor_rank_of_mentee,
    Mentee_corp_id, Mentor_corp_id, 
    Matched_mentor_last_year,
    Algorithm_Same_Match)

## Find where multiple mentees matched to a mentor
match_full_stat_frm_multiple_mentee_cos_sim <- 
  match_full_stat_frm_cos_sim %>% 
  group_by(GaleShapley_Matched_Mentor_Name) %>% 
  add_count() %>% 
  ungroup() %>% 
  dplyr::filter(n > 1) %>% 
  select(-n) %>% 
  arrange(GaleShapley_Matched_Mentor_Name)

match_full_stat_frm_multiple_mentee_cos_sim <- 
  match_full_stat_frm_multiple_mentee_cos_sim %>% 
  group_by(GaleShapley_Matched_Mentor_Name, Mentor_corp_id) %>%
  summarise(
    Mentee.Name = case_when(
      n() == 1 ~ first(Mentee.Name),
      n() == 2 ~ paste(first(Mentee.Name), "and", last(Mentee.Name)),
      # do not know if this works (> 2 not needed as of 2024)
      n() > 2 ~ paste0(
        paste(head(Mentee.Name, -1), collapse = ", "),
        ", and ",
        last(Mentee.Name)
        )
      ),
    Mentee_corp_id = case_when(
      n() == 1 ~ first(Mentee_corp_id),
      n() == 2 ~ paste(first(Mentee_corp_id), "and", last(Mentee_corp_id)),
      # do not know if this works (> 2 not needed as of 2024)
      n() > 2 ~ paste0(
        paste(head(Mentee_corp_id, -1), collapse = ", "),
        ", and ",
        last(Mentee_corp_id)
        )
      )
  ) %>% 
  ungroup() %>% 
  select(GaleShapley_Matched_Mentor_Name, Mentee.Name,
         Mentor_corp_id,  Mentee_corp_id)
```

```{r show_setup4, include = TRUE, echo = TRUE}
rank_role_frm_cos_sim <- 
  bind_rows(
   match_full_stat_frm_cos_sim %>% 
   mutate(Rank = GS_mentor_rank_of_mentee, Role = 'Mentor') %>% 
   select(Rank, Role),
   match_full_stat_frm_cos_sim %>% 
   mutate(Rank = GS_mentee_rank_of_mentor, Role = 'Mentee') %>% 
   select(Rank, Role))
  
```

```{r show_setup3_word_matching, include = TRUE, echo = TRUE}

mentor_mentee_with_word_matching_4pivot_mentee <-
  left_join(
    mentor_mentee_alignment,
    mentor_mentee_alignment_allvars %>% 
              distinct(Mentor.Name, grade_mentor,
                       Mentee.Name, grade_mentee, num_mentees,
                       mentor_above_role)) %>% 
  # mutate(
  #   MW_Pred_compatibility_mentee = 
  #     MW_Pred_compatibility + (personality_mentor_match * mod_mentee)
  #   ) %>% 
  mutate(
    MW_Pred_compatibility_mentee =
      MW_Pred_compatibility
    ) %>%
  group_by(mentee_id) %>%
    mutate(GS_mentee_rank_of_mentor = 
             row_number(desc(MW_Pred_compatibility_mentee))) %>%
  ungroup() %>%
  select(mentor_id, mentee_id, 
         grade_mentor, grade_mentee,
         GS_mentee_rank_of_mentor, 
         MW_Pred_compatibility_mentee)

mentor_mentee_with_word_matching_4pivot_mentor <-
  left_join(
    mentor_mentee_alignment,
    mentor_mentee_alignment_allvars %>% 
              distinct(Mentor.Name, grade_mentor,
                       Mentee.Name, grade_mentee, num_mentees)) %>% 
  group_by(mentor_id) %>%
  mutate(GS_mentor_rank_of_mentee = row_number(desc(MW_Pred_compatibility))) %>%
  ungroup() %>%
  select(mentor_id, mentee_id, 
         GS_mentor_rank_of_mentee, MW_Pred_compatibility, 
         num_mentees)

mentor_mentee_with_word_matching_4pivot <- 
  inner_join(mentor_mentee_with_word_matching_4pivot_mentee,
             mentor_mentee_with_word_matching_4pivot_mentor)

mentor_mentee_alignment_rank_word_matching <- 
  mentor_mentee_with_word_matching_4pivot %>% 
  select(-MW_Pred_compatibility, -MW_Pred_compatibility_mentee,
         -num_mentees)

# sort(sapply(mentor_mentee_alignment_rank, function(x) sum(is.na(x))))

mentor_mentee_with_word_matching <- 
  mentor_mentee_with_word_matching_4pivot %>% 
  select(-MW_Pred_compatibility)

mentor_with_word_matching_pivot <-
  mentor_mentee_with_word_matching_4pivot %>%
  pivot_wider(id_cols = mentor_id, names_from = mentee_id,
              values_from = MW_Pred_compatibility)

mentor_with_alignment_pivot_num_mentees_word_matching <-
  mentor_mentee_with_word_matching_4pivot %>%
  distinct(mentor_id, num_mentees)

num_mentees_slot_word_matching <- 
  mentor_with_alignment_pivot_num_mentees_word_matching %>% 
    mutate(num_mentees = as.double(num_mentees)) %>% 
    pull(num_mentees)

mentee_with_word_matching_pivot <-
  mentor_mentee_with_word_matching_4pivot %>%
  pivot_wider(id_cols = mentee_id, names_from = mentor_id,
              values_from = MW_Pred_compatibility_mentee)

matching_word_matching <- galeShapley.marriageMarket(
  mentee_with_word_matching_pivot %>% select(-mentee_id),
  mentor_with_word_matching_pivot %>% select(-mentor_id)
    )

match_frm_word_matching <- data.frame(matching_word_matching$engagements)

colnames(match_frm_word_matching) <- 'engagements'

match_frm_more_cols_word_matching <- match_frm_word_matching %>%
  mutate(mentee_id = row_number(),
         mentor_id = engagements) %>%
  select(-engagements) %>%
  left_join(mentor_in %>% select(mentor_id, Mentor.Name)) %>%
  left_join(mentee_in %>% select(mentee_id, Mentee.Name,  
                                 Matched_mentor_last_year)) %>% 
  arrange(Mentee.Name) %>%
  mutate(Algorithm_Same_Match = case_when(
    Mentor.Name == Matched_mentor_last_year ~ TRUE,
    TRUE ~ FALSE)) %>%
  relocate(Mentee.Name, Mentor.Name, Matched_mentor_last_year, Algorithm_Same_Match)

match_distribute_frm_word_matching <- match_frm_more_cols_word_matching %>%
  select(Mentee.Name, Mentor.Name, Matched_mentor_last_year, Algorithm_Same_Match) %>%
  rename(GaleShapley_Matched_Mentor_Name = Mentor.Name)

match_full_stat_frm_word_matching <-
  left_join(match_frm_more_cols_word_matching, 
            mentor_mentee_with_word_matching) %>%
  left_join(., mentor_mentee_alignment_allvars0 %>% 
                distinct(Mentor.Name, Mentee.Name,
                         Mentor_corp_id, Mentee_corp_id,
                         grade_mentor, grade_mentee)) %>% 
  dplyr::filter(!is.na(Mentor.Name) & !is.na(Mentee.Name)) %>% 
  rename(GaleShapley_Matched_Mentor_Name = Mentor.Name) %>%
  select(-mentor_id, -mentee_id) %>% 
  relocate(all_of(
    c("grade_mentor", 
      "grade_mentee")),
    .after = "GS_mentee_rank_of_mentor") %>% 
  select(
    Mentee.Name, GaleShapley_Matched_Mentor_Name,
    grade_mentee, grade_mentor,
    GS_mentee_rank_of_mentor, GS_mentor_rank_of_mentee,
    Mentee_corp_id, Mentor_corp_id, 
    Matched_mentor_last_year,
    Algorithm_Same_Match)

## Find where multiple mentees matched to a mentor
match_full_stat_frm_multiple_mentee_word_matching <- 
  match_full_stat_frm_word_matching %>% 
  group_by(GaleShapley_Matched_Mentor_Name) %>% 
  add_count() %>% 
  ungroup() %>% 
  dplyr::filter(n > 1) %>% 
  select(-n) %>% 
  arrange(GaleShapley_Matched_Mentor_Name)

match_full_stat_frm_multiple_mentee_word_matching <- 
  match_full_stat_frm_multiple_mentee_word_matching %>% 
  group_by(GaleShapley_Matched_Mentor_Name, Mentor_corp_id) %>%
  summarise(
    Mentee.Name = case_when(
      n() == 1 ~ first(Mentee.Name),
      n() == 2 ~ paste(first(Mentee.Name), "and", last(Mentee.Name)),
      # do not know if this works (> 2 not needed as of 2024)
      n() > 2 ~ paste0(
        paste(head(Mentee.Name, -1), collapse = ", "),
        ", and ",
        last(Mentee.Name)
        )
      ),
    Mentee_corp_id = case_when(
      n() == 1 ~ first(Mentee_corp_id),
      n() == 2 ~ paste(first(Mentee_corp_id), "and", last(Mentee_corp_id)),
      # do not know if this works (> 2 not needed as of 2024)
      n() > 2 ~ paste0(
        paste(head(Mentee_corp_id, -1), collapse = ", "),
        ", and ",
        last(Mentee_corp_id)
        )
      )
  ) %>% 
  ungroup() %>% 
  select(GaleShapley_Matched_Mentor_Name, Mentee.Name,
         Mentor_corp_id,  Mentee_corp_id)

```

```{r show_setup4_word_matching, include = TRUE, echo = TRUE}

rank_role_frm_word_matching <- 
  bind_rows(
    match_full_stat_frm_word_matching %>% 
      mutate(Rank = GS_mentor_rank_of_mentee, Role = 'Mentor') %>% 
      select(Rank, Role),
    match_full_stat_frm_word_matching %>% 
      mutate(Rank = GS_mentee_rank_of_mentor, Role = 'Mentee') %>% 
      select(Rank, Role))

mentor_matches_mentee_pref_prompt_frm_word_matching <-
  left_join(match_full_stat_frm_word_matching,
            mentee_in %>% distinct(Mentee.Name, mentee_concatenated_responses_no_stopwords),
            multiple = 'all') %>%
  left_join(., mentor_in %>% 
              mutate(GaleShapley_Matched_Mentor_Name = Mentor.Name) %>% 
              distinct(GaleShapley_Matched_Mentor_Name, 
                       mentor_concatenated_responses_no_stopwords)) %>% 
  mutate(Matching_Words = matchwords(mentee_concatenated_responses_no_stopwords,
                                     mentor_concatenated_responses_no_stopwords)) %>%
  distinct(GaleShapley_Matched_Mentor_Name, Mentee.Name, .keep_all = TRUE) %>%
  select(GaleShapley_Matched_Mentor_Name, Mentee.Name,
         mentee_concatenated_responses_no_stopwords, mentor_concatenated_responses_no_stopwords, 
         Matching_Words, GS_mentee_rank_of_mentor) %>%
  arrange(GS_mentee_rank_of_mentor)

```

```{r grade_grade_count_setup, include = TRUE, echo = TRUE}
match_full_grades_cos_sim <- 
  match_full_stat_frm_cos_sim %>% 
   select(grade_mentor, grade_mentee)

match_full_grades_word_matching <- 
  match_full_stat_frm_word_matching %>% 
   select(grade_mentor, grade_mentee)            

match_full_grades_word_matching_table <-
  match_full_grades_word_matching %>%
      ungroup() %>% 
      mutate(grade_mentor = factor(grade_mentor, 
                                         levels = c(paste0("Grade ", 1:9),            
                                                    paste0("Grade ", 10)),
                                         labels = c(paste0("Grade ", 1:9),   
                                                    paste0("Grade ", 10)))) %>% 
      janitor::tabyl(grade_mentor, grade_mentee) %>%
      janitor::adorn_totals("row") %>%
      janitor::adorn_totals("col") %>%
      janitor::adorn_percentages("all") %>% 
      janitor::adorn_pct_formatting(digits = 1) %>%
      janitor::adorn_ns() %>% 
      janitor::adorn_title()

match_full_grades_cos_sim_table <-
  match_full_grades_cos_sim %>%
      ungroup() %>% 
      mutate(grade_mentor = factor(grade_mentor, 
                                         levels = c(paste0("Grade ", 1:9),            
                                                    paste0("Grade ", 10)),
                                         labels = c(paste0("Grade ", 1:9),   
                                                    paste0("Grade ", 10)))) %>% 
      janitor::tabyl(grade_mentor, grade_mentee) %>%
      janitor::adorn_totals("row") %>%
      janitor::adorn_totals("col") %>%
      janitor::adorn_percentages("all") %>% 
      janitor::adorn_pct_formatting(digits = 1) %>%
      janitor::adorn_ns() %>% 
      janitor::adorn_title()

match_full_grades_count_cos_sim <- 
  match_full_grades_cos_sim %>% 
  count(grade_mentor, grade_mentee) %>% 
  mutate(pct = n/sum(n)*100)

match_full_grades_count_word_matching <- 
  match_full_grades_word_matching %>% 
  count(grade_mentor, grade_mentee) %>% 
  mutate(pct = n/sum(n)*100)
```

# Grade : Grade Distribution
This section appears near the top to aid assessment. The Cosine Similarity and Matching Words techniques used are described further below.

## Mentees' Preferences of Relative Mentor Grade
```{r grade_grade_pref_mentee, include = TRUE, echo = TRUE}
mentee_grade_pref <- 
  mentor_mentee_alignment_allvars0 %>% 
  distinct(Mentee.Name, grade_mentee, mentor_above_role)

mentee_grade_pref_tbl <- mentee_grade_pref %>% 
  janitor::tabyl(grade_mentee, mentor_above_role) %>% 
  janitor::adorn_totals("row") %>%
  janitor::adorn_totals("col") %>%
  janitor::adorn_percentages("all") %>% 
  janitor::adorn_pct_formatting(digits = 1) %>%
  janitor::adorn_ns() %>% 
  janitor::adorn_title()

kable(mentee_grade_pref_tbl,
      caption = paste0("Year ", year, ": Preference of Mentees: Higher Grade Mentor?")) %>% 
  kable_styling(bootstrap_options = c("condensed", "striped",
                                        "bordered"),
                  full_width = FALSE) %>%
  column_spec(1, bold = TRUE) %>%
  row_spec(1, bold = TRUE) 
```

## Grade : Grade Bar Charts

```{r grade_grade_count_bar, include = TRUE, echo = TRUE, eval = params$heavy}

ggplot(match_full_grades_count_cos_sim %>% 
         mutate(
           grade_mentor_num = 
           as.numeric(
             str_extract(grade_mentor, "\\d+")),
         grade_mentee_num = 
           as.numeric(
             str_extract(grade_mentee, "\\d+"))) %>% 
         mutate(
           grade_mentor = fct_reorder(grade_mentor, grade_mentor_num),
           grade_mentee = fct_reorder(grade_mentee, grade_mentee_num)),
  aes(y=grade_mentor, label=paste0(round(pct, digits=1)), x=pct)) + 
  geom_col(aes(x=pct, fill=as.factor(grade_mentee))) +
  scale_fill_viridis_d(direction = -1) +
  labs(y="Mentor Grade", x="", title=str_wrap("Grade:Grade Cosine Similarity Pairing", width =60),
       subtitle = year) +
  guides(fill=guide_legend(title="Mentee Grade"))+ 
  scale_y_discrete(labels = c(sort(unique(match_full_grades_count_word_matching$grade_mentor)))) + 
  geom_text(aes(group=as.factor(grade_mentee)), 
            size = 4, position = position_stack(vjust = 0.5, reverse=FALSE),   
            colour="white")

ggplot(match_full_grades_count_word_matching %>% 
         mutate(
           grade_mentor_num = 
           as.numeric(
             str_extract(grade_mentor, "\\d+")),
         grade_mentee_num = 
           as.numeric(
             str_extract(grade_mentee, "\\d+"))) %>% 
         mutate(
           grade_mentor = fct_reorder(grade_mentor, grade_mentor_num),
           grade_mentee = fct_reorder(grade_mentee, grade_mentee_num)),
  aes(y=grade_mentor, label=paste0(round(pct, digits=1)), x=pct)) + 
  geom_col(aes(x=pct, fill=as.factor(grade_mentee))) +
  scale_fill_viridis_d(direction = -1) +
  labs(y="Mentor Grade", x="", title=str_wrap("Grade:Grade Matching Words Pairing", width =60),
       subtitle = year) +
  guides(fill=guide_legend(title="Mentee Grade"))+ 
  scale_y_discrete(labels = c(sort(unique(match_full_grades_count_word_matching$grade_mentor)))) + 
  geom_text(aes(group=as.factor(grade_mentee)), 
            size = 4, position = position_stack(vjust = 0.5, reverse=FALSE),   
            colour="white")
```

## Grade : Grade Tables

```{r grade_grade_count_tbl, include = TRUE, echo = TRUE}
kable(match_full_grades_cos_sim_table,
      caption = paste0("Year ", year, ": Cosine Similarity")) %>% 
    kable_styling(bootstrap_options = c("condensed", "striped",
                                        "bordered"),
                  full_width = FALSE) %>%
    column_spec(1, bold = TRUE) %>%  
    row_spec(1, bold = TRUE) 

kable(match_full_grades_word_matching_table,
      caption = paste0("Year ", year, ": Matching Words")) %>% 
  kable_styling(bootstrap_options = c("condensed", "striped",
                                        "bordered"),
                  full_width = FALSE) %>%
    column_spec(1, bold = TRUE) %>%  
    row_spec(1, bold = TRUE) 

match_full_stat_frm_word_matching_grade_comp <- 
  left_join(match_full_stat_frm_word_matching,
            mentor_mentee_alignment_allvars %>% 
              distinct(Mentee.Name, Mentor.Name, mentor_above_role,
                       grade_mentee_num, 
                       grade_mentor_num),
            by = c('GaleShapley_Matched_Mentor_Name' = 'Mentor.Name',
                   'Mentee.Name')) %>% 
  mutate(
    mentor_to_mentee_grade_comparison = case_when(
      grade_mentor_num > grade_mentee_num ~ "Higher Grade Mentor",
      grade_mentor_num < grade_mentee_num ~ "Lower Grade Mentor",
      grade_mentor_num == grade_mentee_num ~ "Same Grade Mentor"),
    mentor_minus_mentee_grade_diff = 
      grade_mentor_num - grade_mentee_num) 

match_full_stat_frm_word_matching_grade_tbl <-
  match_full_stat_frm_word_matching_grade_comp %>%
      janitor::tabyl(mentor_to_mentee_grade_comparison) %>% 
      janitor::adorn_pct_formatting(digits = 2) 

match_full_stat_frm_cos_sim_grade_comp <- 
  left_join(match_full_stat_frm_cos_sim,
            mentor_mentee_alignment_allvars %>% 
              distinct(Mentee.Name, Mentor.Name, mentor_above_role,
                       grade_mentee_num, grade_mentor_num),
            by = c('GaleShapley_Matched_Mentor_Name' = 'Mentor.Name',
                   'Mentee.Name')) %>% 
  mutate(
    mentor_to_mentee_grade_comparison = case_when(
      grade_mentor_num > grade_mentee_num ~ "Higher Grade Mentor",
      grade_mentor_num < grade_mentee_num ~ "Lower Grade Mentor",
      grade_mentor_num == grade_mentee_num ~ "Same Grade Mentor"),
    mentor_minus_mentee_grade_diff = 
      grade_mentor_num - grade_mentee_num) 

match_full_stat_frm_cos_sim_grade_tbl <-
  match_full_stat_frm_cos_sim_grade_comp %>%
      janitor::tabyl(mentor_to_mentee_grade_comparison) %>% 
      janitor::adorn_pct_formatting(digits = 2) 

kable(match_full_stat_frm_cos_sim_grade_tbl,
      caption = "Cosine Similarity") %>% 
  kable_styling(bootstrap_options = c("condensed", "striped",
                                        "bordered"),
                  full_width = FALSE) %>%
  column_spec(1, bold = TRUE) 

kable(match_full_stat_frm_word_matching_grade_tbl,
      caption = "Matching Words") %>% 
  kable_styling(bootstrap_options = c("condensed", "striped",
                                        "bordered"),
                  full_width = FALSE) %>%
  column_spec(1, bold = TRUE) 

```

## Lower Grade Matched - Table

Summarizing where the mentor's grade is *lower* than the grade of the matched mentee.

```{r lower_grade_tbl, include = TRUE, echo = TRUE, eval = FALSE, eval = params$heavy}
match_full_stat_frm_word_matching_Lower_grade_mentor <- 
  match_full_stat_frm_word_matching_grade_comp %>% 
  dplyr::filter(grade_mentor_num < grade_mentee_num) %>% 
  select(Mentee.Name, GaleShapley_Matched_Mentor_Name, 
         grade_mentee, grade_mentor,
         mentor_to_mentee_grade_comparison,
         mentor_above_role) %>% 
  rename(Prefer_Mentor_Higher_Grade = mentor_above_role)
  
match_full_stat_frm_cos_sim_Lower_grade_mentor <-
  match_full_stat_frm_cos_sim_grade_comp %>% 
  dplyr::filter(grade_mentor_num < grade_mentee_num) %>% 
  select(Mentee.Name, GaleShapley_Matched_Mentor_Name, 
         grade_mentee, grade_mentor,
         mentor_to_mentee_grade_comparison,
         mentor_above_role) %>% 
  rename(Prefer_Mentor_Higher_Grade = mentor_above_role)

match_full_stat_frm_word_matching_Lower_grade_mentor_table <-
  match_full_stat_frm_word_matching_Lower_grade_mentor %>% 
    mutate(
      grade_mentor_num = 
            as.numeric(
             str_extract(grade_mentor, "\\d+")),
      grade_mentee_num = 
            as.numeric(
             str_extract(grade_mentee, "\\d+")),
      mentor_to_mentee_grade_comparison = case_when(
        grade_mentor_num > grade_mentee_num ~ "Higher Grade Mentor",
        grade_mentor_num < grade_mentee_num ~ "Lower Grade Mentor",
        grade_mentor_num == grade_mentee_num ~ "Same Grade Mentor")
    ) 

match_full_stat_frm_cos_sim_Lower_grade_mentor_table <-
  match_full_stat_frm_cos_sim_Lower_grade_mentor %>% 
    mutate(
      grade_mentor_num = 
            as.numeric(
             str_extract(grade_mentor, "\\d+")),
      grade_mentee_num = 
            as.numeric(
             str_extract(grade_mentee, "\\d+")),
      mentor_to_mentee_grade_comparison = case_when(
        grade_mentor_num > grade_mentee_num ~ "Higher Grade Mentor",
        grade_mentor_num < grade_mentee_num ~ "Lower Grade Mentor",
        grade_mentor_num == grade_mentee_num ~ "Same Grade Mentor")
    ) 

if (nrow(match_full_stat_frm_cos_sim_Lower_grade_mentor_table) == 0) {
  cat("No lower grade mentors appeared in Cosine Similarity pairings")
} else {
  kable(match_full_stat_frm_cos_sim_Lower_grade_mentor_table,
      caption = "Lower Grade Mentor : Cosine Similarity") %>% 
  kable_styling(bootstrap_options = c("condensed", "striped",
                                        "bordered"),
                  full_width = FALSE) %>%
  column_spec(1, bold = TRUE) 
}

if (nrow(match_full_stat_frm_word_matching_Lower_grade_mentor_table) == 0) {
  cat("No lower grade mentors appeared in Matching Words pairings")
} else {
    kable(match_full_stat_frm_word_matching_Lower_grade_mentor_table,
          caption = "Lower Grade Mentor : Matching Words") %>% 
      kable_styling(bootstrap_options = c("condensed", "striped",
                                          "bordered"),
                    full_width = FALSE) %>%
      column_spec(1, bold = TRUE)
}

```

## Same Grade Matched - Table

```{r same_grade, include = TRUE, echo = TRUE, eval = FALSE, eval = params$heavy}
match_full_stat_frm_word_matching_Same_grade_mentor <- 
  left_join(match_full_stat_frm_word_matching_grade_comp,
            mentor_mentee_alignment_allvars0 %>% 
              distinct(Mentor.Name, Mentee.Name, mentor_above_role) %>% 
              rename(GaleShapley_Matched_Mentor_Name = Mentor.Name)) %>% 
  dplyr::filter(grade_mentor_num == grade_mentee_num) %>% 
  select(Mentee.Name, GaleShapley_Matched_Mentor_Name, 
         grade_mentee, grade_mentor,
         mentor_above_role,
         mentor_to_mentee_grade_comparison) %>% 
  rename(prefer_mentor_above_role = mentor_above_role)

match_full_stat_frm_cos_sim_Same_grade_mentor <-
  left_join(match_full_stat_frm_cos_sim_grade_comp,
            mentor_mentee_alignment_allvars0 %>% 
              distinct(Mentor.Name, Mentee.Name, mentor_above_role) %>% 
              rename(GaleShapley_Matched_Mentor_Name = Mentor.Name)) %>% 
  dplyr::filter(grade_mentor_num == grade_mentee_num) %>% 
  select(Mentee.Name, GaleShapley_Matched_Mentor_Name, 
         grade_mentee, grade_mentor,
         mentor_above_role,
         mentor_to_mentee_grade_comparison) %>% 
  rename(prefer_mentor_above_role = mentor_above_role)

match_full_stat_frm_word_matching_Same_grade_mentor_table <-
  match_full_stat_frm_word_matching_Same_grade_mentor %>% 
    janitor::tabyl(prefer_mentor_above_role, grade_mentor) %>%
    janitor::adorn_totals("row") %>%
    janitor::adorn_totals("col") %>%
    janitor::adorn_percentages("all") %>% 
    janitor::adorn_pct_formatting(digits = 1) %>%
    janitor::adorn_ns() %>% 
    janitor::adorn_title()

match_full_stat_frm_cos_sim_Same_grade_mentor_table <-
  match_full_stat_frm_cos_sim_Same_grade_mentor %>% 
    janitor::tabyl(prefer_mentor_above_role, grade_mentor) %>%
    janitor::adorn_totals("row") %>%
    janitor::adorn_totals("col") %>%
    janitor::adorn_percentages("all") %>% 
    janitor::adorn_pct_formatting(digits = 1) %>%
    janitor::adorn_ns() %>% 
    janitor::adorn_title()

kable(match_full_stat_frm_cos_sim_Same_grade_mentor_table,
      caption = "Same Grade Mentor : Cosine Similarity") %>% 
  kable_styling(bootstrap_options = c("condensed", "striped",
                                        "bordered"),
                  full_width = FALSE) %>%
  column_spec(1, bold = TRUE) %>%
  row_spec(1, bold = TRUE) 

kable(match_full_stat_frm_word_matching_Same_grade_mentor_table,
      caption = "Same Grade Mentor : Matching Words") %>% 
  kable_styling(bootstrap_options = c("condensed", "striped",
                                        "bordered"),
                  full_width = FALSE) %>%
  column_spec(1, bold = TRUE) %>%
  row_spec(1, bold = TRUE) 
```

# Quality of Matches

## Statistics Table: Quality of Matches

```{r quality_match, include = TRUE, echo = TRUE}
summary_match_qual_cos_sim <-
  round(
    t(
      do.call(cbind,
        lapply(match_full_stat_frm_cos_sim %>% 
                 select(GS_mentor_rank_of_mentee,
                        GS_mentee_rank_of_mentor),
               function(x) quantile(x, probs = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1), na.rm = TRUE)))  # Calculate deciles and including Min (0%) and Max (100%)
    ),
  2)

colnames(summary_match_qual_cos_sim) <- c("Min", "10%", "20%", "30%", "40%", "Median", "60%", "70%", "80%", "90%", "Max") 

#### Table summarizing match quality : Word Matching
summary_match_qual_word_matching <-
  round(
    t(
      do.call(cbind,
        lapply(match_full_stat_frm_word_matching %>% 
                 select(GS_mentor_rank_of_mentee,
                        GS_mentee_rank_of_mentor),
               function(x) quantile(x, probs = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1), na.rm = TRUE)))
    ),
  2)

colnames(summary_match_qual_word_matching) <- c("Min", "10%", "20%", "30%", "40%", "Median", "60%", "70%", "80%", "90%", "Max") 
# delete to 1593
percentile_breaks <- seq(0, 100, by = 5)

# 1) Pull ranks (lower is better)
mentee_ranks_cos_sim <- match_full_stat_frm_cos_sim %>%
  pull(GS_mentee_rank_of_mentor)
mentee_ranks_word_matching <- match_full_stat_frm_word_matching %>%
  pull(GS_mentee_rank_of_mentor)

#' Bin ranks with a special rank==1 bin and then percentile steps on 2..max_rank
#' @param ranks Numeric vector of ranks (lower is better). Can contain NA.
#' @param pct_steps Numeric vector of percentile steps (default seq(0.05, 1, 0.05)).
#' @return List with bins (factor), bin_counts (integer vector), cum_percent (numeric),
#'         and wide_table (1-row data.frame of cumulative percentages).
bin_ranks_with_percentiles <- function(ranks, pct_steps = seq(0.05, 1.00, by = 0.05)) {
  ranks <- as.numeric(ranks)
  max_rank <- suppressWarnings(max(ranks, na.rm = TRUE))
  if (is.infinite(max_rank)) max_rank <- NA_real_
  
  # Validate
  if (is.na(max_rank)) {
    stop("No valid ranks found (all NA).")
  }
  
  # Construct breaks and labels
  if (max_rank <= 1) {
    breaks <- c(0.5, 1.5)
    bin_labels <- "0ile"
  } else {
    boundary_ranks_after1 <- 1 + ceiling(pct_steps * (max_rank - 1))
    breaks <- c(0.5, 1.5, boundary_ranks_after1 + 0.5)
    bin_labels <- c("0ile", paste0(sprintf("%0.f", pct_steps * 100), "ile"))
  }
  
  # Bin
  bins <- cut(ranks, breaks = breaks, labels = bin_labels,
              include.lowest = TRUE, right = TRUE)
  
  # Counts: preserve zero-levels
  bin_counts <- as.integer(table(factor(bins, levels = bin_labels)))
  
  # Cumulative % over non-NA ranks
  valid_n <- sum(!is.na(ranks))
  cum_percent <- if (valid_n > 0) 100 * cumsum(bin_counts) / valid_n else rep(NA_real_, length(bin_counts))
  
  # Wide table
  wide_table <- as.data.frame(t(round(cum_percent, 1)))
  colnames(wide_table) <- bin_labels
  
  list(
    bins = bins,
    bin_counts = bin_counts,
    cum_percent = cum_percent,
    wide_table = wide_table
  )
}

wide_table_percentile_cos_sim <- bin_ranks_with_percentiles(mentee_ranks_cos_sim)[[4]]
wide_table_percentile_word_matching <- bin_ranks_with_percentiles(mentee_ranks_word_matching)[[4]]
```

```{r quality_match_table, include = TRUE, echo = TRUE, eval = params$heavy}

kable(summary_match_qual_cos_sim,
      caption = paste0("Year ", year, ": Cosine Similarity pairings: ")) %>% 
  kable_styling(bootstrap_options = c("condensed", "striped", "bordered"),
                full_width = F)

# Extract the value under "20ile" and round it
percent_20ile <- round(wide_table_percentile_cos_sim[["20ile"]], 0)

caption_text <- paste0(year, ": Cosine Similarity pairing - predicted compatibility of mentor percentiles for mentees. ", "For example, ", percent_20ile, "% of the mentees matched with a mentor among the top 20% most compatible. 0ile represents the single mentor predicted to be most compatible." )

# Display the table with the caption
kable(wide_table_percentile_cos_sim,
      caption = caption_text) %>%
  kable_styling(bootstrap_options = c("condensed", "striped", "bordered"), 
                full_width = FALSE)

kable(summary_match_qual_word_matching,
      caption = paste0("Year ", year, ": Matching Words pairings: ")) %>% 
  kable_styling(bootstrap_options = c("condensed", "striped", "bordered"), 
                 full_width = F)

# Extract the value under "20ile" and round it
percent_20ile <- round(wide_table_percentile_word_matching[["20ile"]], 0)

caption_text <- paste0(year, ": Matching Words pairing - predicted compatibility of mentor percentiles for mentees. ", "For example, ", percent_20ile, "% of the mentees matched with a mentor among the top 20% most compatible. 0ile represents the single mentor predicted to be most compatible.")

# Display the table with the caption
kable(wide_table_percentile_word_matching,
      caption = caption_text) %>%
  kable_styling(bootstrap_options = c("condensed", "striped", "bordered"), 
                full_width = FALSE)

```

```{r per_grade_fairness}

# ---- Fairness: mentor percentile by grade ----
library(dplyr)
library(stringr)
library(tidyr)
library(flextable)
library(purrr)

# Choose the grade dimension to test fairness across
grade_col <- "grade_mentee"   # change to "grade_mentor" if desired

# Build mentor percentile (0–100) from ranks for Word Matching frame
fair_df_word_matching <- match_full_stat_frm_word_matching %>%
  mutate(
    # rank is 1=best; convert to percentile of *predicted compatibility from mentee’s perspective*
    mentee_rank = GS_mentee_rank_of_mentor,
    # max possible rank equals candidate count visible to the mentee
    max_rank    = max(mentee_rank, na.rm = TRUE),
    mentor_percentile = 100 * ((mentee_rank - 1) / (max_rank - 1)) # best rank = 0
    # Note: If ties exist or exact 0/100 are problematic, you can use (rank-0.5)/max_rank then *100
  ) %>%
  filter(!is.na(mentor_percentile), !is.na(grade_mentee)) %>%
  mutate(
    grade_stratum = factor(grade_mentee, levels = sort(unique(grade_mentee))),
    method = factor("Matching Words", levels = c("Cosine Similarity", "Matching Words")),
    u = u
  )

# Build mentor percentile (0–100) from ranks for Cosine Similarity frame
fair_df_cos_sim <- match_full_stat_frm_cos_sim %>%
  mutate(
    # rank is 1=best; convert to percentile of *predicted compatibility from mentee’s perspective*
    mentee_rank = GS_mentee_rank_of_mentor,
    # max possible rank equals candidate count visible to the mentee
    max_rank    = max(mentee_rank, na.rm = TRUE),
    mentor_percentile = 100 * ((mentee_rank - 1) / (max_rank - 1)) # best rank = 0
    # Note: If ties exist or exact 0/100 are problematic, you can use (rank-0.5)/max_rank then *100
  ) %>%
  filter(!is.na(mentor_percentile), !is.na(grade_mentee)) %>%
  mutate(
    grade_stratum = factor(grade_mentee, levels = sort(unique(grade_mentee))),
    method = factor("Cosine Similarity", levels = c("Cosine Similarity", "Matching Words")),
    u = u
  )
```

## `r year`: Density Plot (Rank of Matches): Cosine Similarity

A rank of 1 would mean that the individual was paired with the mentor or mentee of highest predicted compatibility.

```{r density plot, eval = params$heavy}
## https://jtr13.github.io/cc20/brief-introduction-and-tutorial-of-ggpubr-package.html
ggdensity(rank_role_frm_cos_sim, x = "Rank",
   rug = TRUE,
   color = "Role", fill = "Role") +
   labs(subtitle = year) 

```

## `r year`: Density Plot (Rank of Matches): Matching Words

A rank of 1 would mean that the individual was paired with the mentor or mentee of highest predicted compatibility.

```{r density plot_word_matching, eval = params$heavy}
## https://jtr13.github.io/cc20/brief-introduction-and-tutorial-of-ggpubr-package.html
ggdensity(rank_role_frm_word_matching, x = "Rank",
          rug = TRUE,
          color = "Role", fill = "Role") +
   labs(subtitle = year) 
```

# Unmatched mentors or mentees

These individuals were not matched with a person of the opposite category (mentor / mentee) because of insufficient numbers.

```{r unmatched, include = TRUE, echo = TRUE, eval = params$heavy}
missing_for_mentee_cos_sim <- 
  anti_join(
    mentor_mentee_alignment_allvars0 %>% 
      distinct(Mentee.Name, grade_mentee_num, Mentee_free_text_responses_number_of_characters),
    match_distribute_frm_cos_sim %>% 
      filter(!is.na(GaleShapley_Matched_Mentor_Name)) %>% 
      distinct(Mentee.Name)) %>% 
  rename(Name = Mentee.Name,
         free_text_responses_number_of_characters = Mentee_free_text_responses_number_of_characters) %>% 
  mutate (Name = "Dummy") %>% 
  mutate(Desired_Role = "Mentee",
                Grade = grade_mentee_num) %>% 
  select(Name, Desired_Role, Grade, free_text_responses_number_of_characters)

missing_for_mentor_cos_sim <- 
  anti_join(
    mentor_mentee_alignment_allvars0 %>% 
      distinct(Mentor.Name, grade_mentor_num, Mentor_free_text_responses_number_of_characters),
    match_distribute_frm_cos_sim %>% 
        filter(!is.na(Mentee.Name)) %>% 
        distinct(GaleShapley_Matched_Mentor_Name),
    by = c('Mentor.Name' = 'GaleShapley_Matched_Mentor_Name')) %>% 
  rename(Name = Mentor.Name,
         free_text_responses_number_of_characters = Mentor_free_text_responses_number_of_characters) %>% 
  mutate(Desired_Role = "Mentor",
                Grade = grade_mentor_num) %>% 
  mutate (Name = "Dummy") %>% 
  select(Name, Desired_Role, Grade, free_text_responses_number_of_characters)

missing_for_mentee_word_matching <- 
  anti_join(
    mentor_mentee_alignment_allvars0 %>% 
      distinct(Mentee.Name, grade_mentee_num, Mentee_free_text_responses_number_of_characters),
    match_distribute_frm_word_matching %>% 
      filter(!is.na(GaleShapley_Matched_Mentor_Name)) %>% 
      distinct(Mentee.Name)) %>% 
  rename(Name = Mentee.Name,
         free_text_responses_number_of_characters = Mentee_free_text_responses_number_of_characters) %>% 
  mutate(Desired_Role = "Mentee",
                Grade = grade_mentee_num) %>% 
  mutate (Name = "Dummy") %>% 
  select(Name, Desired_Role, Grade, free_text_responses_number_of_characters)

missing_for_mentor_word_matching <- 
  anti_join(
    mentor_mentee_alignment_allvars0 %>% 
      distinct(Mentor.Name, grade_mentor_num, Mentor_free_text_responses_number_of_characters),
    match_distribute_frm_word_matching %>% 
        filter(!is.na(Mentee.Name)) %>% 
        distinct(GaleShapley_Matched_Mentor_Name),
    by = c('Mentor.Name' = 'GaleShapley_Matched_Mentor_Name')) %>% 
  rename(Name = Mentor.Name,
         free_text_responses_number_of_characters = Mentor_free_text_responses_number_of_characters) %>% 
  mutate(Desired_Role = "Mentor",
                Grade = grade_mentor_num) %>% 
  mutate (Name = "Dummy") %>% 
  select(Name, Desired_Role, Grade, free_text_responses_number_of_characters)

missing_for_cos_sim <-
  rbind(missing_for_mentor_cos_sim,
        missing_for_mentee_cos_sim)

missing_for_word_matching <-
  rbind(missing_for_mentor_word_matching,
        missing_for_mentee_word_matching)

kable(missing_for_cos_sim,
      caption = "Cosine Similarity: Unmatched") %>% 
  kable_styling(bootstrap_options = c("condensed", "striped",
                                        "bordered"),
                  full_width = FALSE) %>%
  column_spec(1, bold = TRUE) 

kable(missing_for_word_matching,
      caption = "Matching Words: Unmatched") %>% 
  kable_styling(bootstrap_options = c("condensed", "striped",
                                        "bordered"),
                  full_width = FALSE) %>%
  column_spec(1, bold = TRUE)
```

## Free Text Responses - Number of Characters (Matched Vs. Unmatched Prospective Mentees)

If "Unmatched" does not appear below, all mentees were matched with a mentor.

```{r free_text_summary, include = TRUE, echo = TRUE, eval = params$heavy}
free_text_length_cos_sim_base <-
  rbind(
    missing_for_cos_sim %>% 
      select(Name, Grade, free_text_responses_number_of_characters) %>% 
      mutate(Status = "Unmatched"),
    anti_join(mentor_mentee_alignment_allvars0 %>% 
                rename(Name = Mentee.Name,
                       Grade = grade_mentee_num,
                       free_text_responses_number_of_characters =
                         Mentee_free_text_responses_number_of_characters) %>% 
                distinct(Name, Grade, free_text_responses_number_of_characters),
              missing_for_cos_sim %>% 
                distinct(Name, Grade)
              ) %>% 
    mutate(Status = "Matched")
  ) %>% 
  select(-Name)

free_text_length_word_matching_base <-
  rbind(
    missing_for_word_matching %>% 
      select(Name, Grade, free_text_responses_number_of_characters) %>% 
      mutate(Status = "Unmatched"),
    anti_join(mentor_mentee_alignment_allvars0 %>% 
                rename(Name = Mentee.Name,
                       Grade = grade_mentee_num,
                       free_text_responses_number_of_characters =
                         Mentee_free_text_responses_number_of_characters) %>% 
                distinct(Name, Grade, free_text_responses_number_of_characters),
              missing_for_word_matching %>% 
                distinct(Name, Grade)
              ) %>% 
    mutate(Status = "Matched")
  )

free_text_length_cos_sim <- 
  free_text_length_cos_sim_base %>%
    group_by(Grade, Status) %>%
    summarise(
      Min = round(min(free_text_responses_number_of_characters), 1),
      Mean = round(mean(free_text_responses_number_of_characters), 1),
      Median = round(median(free_text_responses_number_of_characters), 1),
      Max = round(max(free_text_responses_number_of_characters), 1)
    ) %>% 
  ungroup()

free_text_length_cos_sim_status_only <- 
  free_text_length_cos_sim_base %>%
    group_by(Status) %>%
    summarise(
      Min = round(min(free_text_responses_number_of_characters), 1),
      Mean = round(mean(free_text_responses_number_of_characters), 1),
      Median = round(median(free_text_responses_number_of_characters), 1),
      Max = round(max(free_text_responses_number_of_characters), 1)
    ) %>% 
  ungroup()

free_text_length_word_matching <- 
  free_text_length_word_matching_base %>%
    group_by(Grade, Status) %>%
    summarise(
      Min = round(min(free_text_responses_number_of_characters), 1),
      Mean = round(mean(free_text_responses_number_of_characters), 1),
      Median = round(median(free_text_responses_number_of_characters), 1),
      Max = round(max(free_text_responses_number_of_characters), 1)
    ) %>% 
  ungroup()

free_text_length_word_matching_status_only <- 
  free_text_length_word_matching_base %>%
    group_by(Status) %>%
    summarise(
      Min = round(min(free_text_responses_number_of_characters), 1),
      Mean = round(mean(free_text_responses_number_of_characters), 1),
      Median = round(median(free_text_responses_number_of_characters), 1),
      Max = round(max(free_text_responses_number_of_characters), 1)
    ) %>% 
  ungroup()

kable(free_text_length_cos_sim,
      caption = "Cosine Similarity pairing - Length of Free Text Responses") %>% 
  kable_styling(bootstrap_options = c("condensed", "striped", "bordered"),
                full_width = F)

kable(free_text_length_word_matching,
      caption = "Matching Words pairing - Length of Free Text Responses") %>% 
  kable_styling(bootstrap_options = c("condensed", "striped", "bordered"), 
                 full_width = F)

kable(free_text_length_cos_sim_status_only,
      caption = "Cosine Similarity pairing - Length of Free Text Responses (overall)") %>%
  kable_styling(bootstrap_options = c("condensed", "striped", "bordered"),
                full_width = F)

kable(free_text_length_word_matching_status_only,
      caption = "Matching Words pairing - Length of Free Text Responses (overall)") %>%
  kable_styling(bootstrap_options = c("condensed", "striped", "bordered"), 
                 full_width = F)
```

# Correlations of mentor:mentee Comparison Metrics

The *Cosine Similarity* and *Matching Words* ranking used to rank and then Gale-Shapley pair mentors and mentees were modified for only the mentee when their introverted/extroverted preference was matched by the mentor's self-identification.

Otherwise, tney were generally modified based on considerations of survey response alignment like the intro/extro preference and the degree to which the mentor's indicated strongest skills aligned with the skills the mentee most wanted to improve.

These correlations are for the metrics prior to the heavy penalty if the same mentor was matched as last year. 

```{r comparison2, include = TRUE, echo = TRUE}

all_match_types <- 
  mentor_mentee_alignment_allvars %>% 
  ungroup() %>% 
  distinct(Mentor.Name, Mentee.Name, .keep_all = TRUE) %>% 
  left_join(
    .,
    mentor_mentee_alignment_rank_cos_sim_4pivot %>% 
      distinct(mentor_id, mentee_id, 
               CS_Pred_compatibility)) %>% 
  left_join(
    .,
    mentor_mentee_with_word_matching_4pivot %>% 
      distinct(mentor_id, mentee_id, 
               MW_Pred_compatibility)) %>% 
  select(-mentor_concatenated_responses_chars,
         -num_mentees, -mentor_id, -mentee_id,
         -concatenated_responses_num_mentor_minus_mentee) %>% 
  select_if(is.numeric)

correlation::correlation(all_match_types) %>% 
  dplyr::filter(Parameter2 == 'CS_Pred_compatibility') %>% 
  arrange(desc(r))

correlation::correlation(all_match_types) %>% 
  dplyr::filter(Parameter2 == 'CS_Pred_compatibility_mentee') %>% 
  arrange(desc(r))

correlation::correlation(all_match_types) %>% 
  dplyr::filter(Parameter2 == 'MW_Pred_compatibility') %>% 
  arrange(desc(r))

correlation::correlation(all_match_types) %>% 
  dplyr::filter(Parameter2 == 'MW_Pred_compatibility_mentee') %>% 
  arrange(desc(r))


df_corr_input <- all_match_types %>%
  select(
           Cosine_Similarity,
           MW_count,
           CS_Pred_compatibility,
           MW_Pred_compatibility,
           mentor_skills_match,
           personality_mentee_match,
           personality_mentor_match,
           grade_subscore,
           BG_match,
           )

wide_table_correlations <- df_corr_input %>%
  mutate(across(everything(), as.numeric)) %>% 
  cor(use = "pairwise.complete.obs", method = "pearson") %>%
  as.data.frame() %>%
  rownames_to_column(var = "variable")
```

```{r comparison2_graph, include = TRUE, echo = TRUE, eval = params$heavy}

ggstatsplot::ggcorrmat(
  all_match_types %>%
     select(
           Cosine_Similarity,
           MW_count,
           CS_Pred_compatibility,
           MW_Pred_compatibility,
           mentor_skills_match,
           personality_mentee_match,
           personality_mentor_match,
           grade_subscore,
           BG_match,
           ),
  title = sprintf("%s: Correlations", year)
)
```

## Mentor Grade Minus Mentee Grade - Tables

```{r grade_grade_count_tbl_diff, include = TRUE, echo = TRUE}
summary_grade_cos_sim <- 
  round(
    t(
      do.call(cbind,
        lapply(match_full_stat_frm_cos_sim_grade_comp %>% 
                 select(mentor_minus_mentee_grade_diff),
               summary))
    ),
  2)
        
summary_grade_word_matching <- 
  round(
    t(
      do.call(cbind,
        lapply(match_full_stat_frm_word_matching_grade_comp %>% 
                 select(mentor_minus_mentee_grade_diff),
               summary))
    ),
  2)

kbl(summary_grade_cos_sim,
    caption = "Cosine Similarity pairing") %>% 
  kable_classic(full_width = F) 

kbl(summary_grade_word_matching,
    caption = "Matching Words pairing") %>% 
  kable_classic(full_width = F) 
```

## Average Mentor / Mentee Grade

```{r avg_grade, include = TRUE, echo = TRUE, eval = params$heavy}

avg_grade_cos_sim <- 
  round(
    t(
      do.call(cbind,
        lapply(match_full_stat_frm_word_matching_grade_comp %>% 
                 select(grade_mentor_num,
                        grade_mentee_num),
               summary))
    ),
  2)

avg_grade_word_matching <- 
  round(
    t(
      do.call(cbind,
        lapply(match_full_stat_frm_cos_sim_grade_comp %>% 
                 select(grade_mentor_num,
                        grade_mentee_num),
               summary))
    ),
  2)

kbl(avg_grade_cos_sim,
    caption = "Cosine Similarity pairing") %>% 
  kable_classic(full_width = F) 

kbl(avg_grade_word_matching,
    caption = "Matching Words pairing") %>% 
  kable_classic(full_width = F) 

```

# Same Matches As The Prior Year

Very unlikely because of scoring penalty when comparing a mentee to the responses of the same mentor as last year.

```{r comparison1, include = TRUE, echo = TRUE}
match_frm_more_cols_same_cos_sim <- 
  match_frm_more_cols_cos_sim %>% 
   mutate(Matching_Type = "Cosine Similarity Mod") %>% 
   group_by(Matching_Type, .drop = FALSE) %>% 
    dplyr::filter(Algorithm_Same_Match == TRUE) %>% 
    summarize(Algorithm_Same_Match_As_Original = n()) %>% 
   ungroup()


match_frm_more_cols_word_matching_same <- 
  match_frm_more_cols_word_matching %>% 
   mutate(Matching_Type = "Matching Words Mod") %>% 
   group_by(Matching_Type, .drop = FALSE) %>% 
    dplyr::filter(Algorithm_Same_Match == TRUE) %>% 
    summarize(Algorithm_Same_Match_As_Original = n()) %>% 
   ungroup()
if(nrow(match_frm_more_cols_word_matching_same) == 0) {
  match_frm_more_cols_word_matching_same$Algorithm_Same_Match_As_Original <- 0
}

all_match_counts <-
  bind_rows(
    match_frm_more_cols_same_cos_sim,
    match_frm_more_cols_word_matching_same)

ggdotchart(all_match_counts, 
           x = "Matching_Type",
           y = "Algorithm_Same_Match_As_Original",
           add = "segments",                             # Add segments from y = 0 to dots
           rotate = TRUE,                                # Rotate vertically
           dot.size = 6,                                 # Large dot size
           label = round(all_match_counts$Algorithm_Same_Match_As_Original),
           font.label = list(color = "white", size = 9, 
                             vjust = 0.5),               # Adjust label parameters
           ggtheme = theme_pubr()                        # ggplot2 theme
           )
    
```

# Discarded participants' data summary (lack of data)

This is the distribution of discarded participants' data. Participants were first discarded (not summarized) if they did not provide a first and last name, did not indicate whether they wanted to be a mentor or mentee, or did not complete the role-specific required survey questions. The only survey questions excluded from that completeness gate are the two anything-to-add or special-considerations text fields.

The next table shows the effect of the new required-response completion gate within this year, by role. It counts only respondents who already passed the identity and role checks, because those are the only rows that can be assigned cleanly to Mentor or Mentee.

```{r required_completion_gate_summary, include = TRUE, echo = TRUE}
kable(
  required_completion_exclusions,
  caption = paste0(
    year,
    ": Required-response completion gate summary by role"
  )
) %>%
  kable_styling(
    bootstrap_options = c("condensed", "striped", "bordered"),
    full_width = FALSE
  ) %>%
  column_spec(1, bold = TRUE) %>%
  row_spec(1, bold = TRUE)
```

Summarized here is one common discarded pattern: participants who did not indicate the introvert or extrovert item for either role. This generally coincides with broader nonresponse.

```{r discarded_participants, include = TRUE, echo = TRUE, eval = params$heavy}

  ## Filters on the extrovert/introvert items the surrounding text describes. It
  ## previously filtered on the personality-description question, which named a
  ## different item and has since been dropped from the instrument entirely.
  no_extra_intro <- surv_results_pre_removal %>%
    dplyr::filter(is.na(would_you_consider_yourself_an_extrovert_or_an_introvert) &
                  is.na(would_you_consider_yourself_an_extrovert_or_an_introvert_2))

if(nrow(no_extra_intro) > 1) {  
  no_extra_intro_tbl <- no_extra_intro %>% 
    janitor::tabyl(what_is_your_grade_level, would_you_like_to_be_a_mentor_or_a_mentee) %>% 
    janitor::adorn_totals("row") %>%
    janitor::adorn_totals("col") %>%
    janitor::adorn_percentages("all") %>% 
    janitor::adorn_pct_formatting(digits = 1) %>%
    janitor::adorn_ns() %>% 
    janitor::adorn_title()
  
  # Add a row number column
  no_extra_intro <- cbind(Row = 1:nrow(no_extra_intro), no_extra_intro)
  
  kable(no_extra_intro %>% 
          select(Row, display_name, would_you_like_to_be_a_mentor_or_a_mentee,
                 what_is_your_grade_level),
        caption = "Discarded Participants (missing data = lack of response)") %>% 
    kable_styling(bootstrap_options = c("condensed", "striped",
                                          "bordered"),
                    full_width = FALSE) 
  
  kable(no_extra_intro_tbl,
        caption = "Discarded Participants (missing data = lack of response)") %>% 
    kable_styling(bootstrap_options = c("condensed", "striped",
                                          "bordered"),
                    full_width = FALSE) %>%
    column_spec(1, bold = TRUE) %>%
    row_spec(1, bold = TRUE) 
}
```

# Artifacts

```{r artifacts, include = TRUE, echo = TRUE}
saveRDS(mentee_ranks_cos_sim,           file = file.path(art_dir_u, sprintf("mentee_ranks_cos_sim_%s.rds", year)))
saveRDS(mentee_ranks_word_matching,     file = file.path(art_dir_u, sprintf("mentee_ranks_word_matching_%s.rds", year)))
saveRDS(wide_table_percentile_cos_sim,  file = file.path(art_dir_u, sprintf("wide_table_percentile_cos_sim_%s.rds", year)))
saveRDS(wide_table_percentile_word_matching, file = file.path(art_dir_u, sprintf("wide_table_percentile_word_matching_%s.rds", year)))
saveRDS(rank_role_frm_cos_sim,          file = file.path(art_dir_u, sprintf("density_plot_cos_sim_%s.rds", year)))
saveRDS(rank_role_frm_word_matching,    file = file.path(art_dir_u, sprintf("density_plot_word_matching_%s.rds", year)))
saveRDS(wide_table_correlations,        file = file.path(art_dir_u, sprintf("wide_table_correlations_%s.rds", year)))
saveRDS(fair_df_word_matching,          file = file.path(art_dir_u, sprintf("fair_df_word_matching_%s.rds", year)))
saveRDS(fair_df_cos_sim,                file = file.path(art_dir_u, sprintf("fair_df_cos_sim_%s.rds", year)))
## Write per-u copy (for traceability) and top-level copy (for cross-year aggregation).
readr::write_csv(
  required_completion_exclusions,
  file.path(art_dir_u, sprintf("required_completion_exclusions_%s.csv", year))
)
readr::write_csv(
  required_completion_exclusions,
  file.path(artifacts_dir, sprintf("exclusion_summary_%d.csv", year))
)

## Eligible-mentor pool sizes.
## The repository's `max_rank` column is max(assigned rank), not the pool size, so the
## candidate-set denominator is not otherwise recoverable from the saved artifacts.
## Every mentee ranks every mentor row, so the per-mentee eligible set is the
## post-duplication mentor pool. Recorded here so downstream scripts need not infer it.
matching_pool <- tibble::tibble(
  year                         = as.integer(year),
  n_mentor_pre_duplication     = as.integer(mentor_starter_rows),
  n_mentor_post_duplication    = as.integer(dplyr::n_distinct(mentor_in$mentor_id)),
  n_mentee                     = as.integer(nrow(mentee_in)),
  n_alignment_rows             = as.integer(nrow(mentor_mentee_alignment)),
  eligible_mentors_per_mentee  = as.integer(
    nrow(mentor_mentee_alignment) / dplyr::n_distinct(mentor_mentee_alignment$mentee_id)
  )
)
stopifnot(
  matching_pool$eligible_mentors_per_mentee == matching_pool$n_mentor_post_duplication
)
readr::write_csv(matching_pool, file.path(art_dir_u, sprintf("matching_pool_%s.csv", year)))
readr::write_csv(matching_pool, file.path(artifacts_dir, sprintf("matching_pool_%d.csv", year)))

## Score-component spread. Records pre-normalisation raw statistics so the
## natural scale of each component remains auditable. With z-score normalisation
## every component enters the combined score at SD = 1 (NLP terms) or u * 1
## (survey-match term), so scaled_sd reflects that rather than a raw multiplier.
score_cols <- intersect(c("Cosine_Similarity", "MW_count", "overall_survey_match_num"),
                        names(mentor_mentee_alignment))
if (length(score_cols) > 0) {
  score_components <- purrr::map_dfr(score_cols, function(cl) {
    v <- as.numeric(mentor_mentee_alignment[[cl]])
    tibble::tibble(
      year = as.integer(year), u = as.numeric(u), component = cl,
      n = sum(!is.na(v)), n_distinct = dplyr::n_distinct(v),
      min = min(v, na.rm = TRUE), max = max(v, na.rm = TRUE),
      mean = mean(v, na.rm = TRUE), sd = stats::sd(v, na.rm = TRUE)
    )
  }) %>%
    dplyr::mutate(
      ## After z-scoring each component has SD=1 in the combined score; the survey
      ## term is further scaled by u, so its effective SD is u. scaled_sd records
      ## that effective contribution (not a raw-units multiplier as in the paper).
      scaled_sd = dplyr::case_when(
        component == "overall_survey_match_num" ~ 1 * u,
        TRUE                                    ~ 1
      )
    )
  readr::write_csv(score_components,
                   file.path(art_dir_u, sprintf("score_components_%s.csv", year)))
}
```

